### 2018-03-03 paper.tex
Add template for midterm paper

\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Scale Space Edge Detection}

\author{
  Nick Draper, Jonathan Hayase\\
  Seminar in Differential Geometry\\
  Harvey Mudd College
}

\begin{document}
\maketitle

\begin{abstract}
  We did some things.
\end{abstract}

\section{}

\section*{References}

\end{document}

### 2018-03-04 paper.tex
started paper

@@
+%&pdflatex
 \documentclass{article}
@@
 \begin{abstract}
-  We did some things.
+    Scale space representation is the idea that a two dimensional image can be represented by a collection of smoothed images.
+This paper documents how using such a representation can be useful for detecting edges in an image.
+The scale space allows for a classification of how strong different edges are in the image from very fine to coarse ones.
 \end{abstract}
 
-\section{}
+\section{Scale Space}
+To understand how exactly we detect images in the scale space, we must first define what the scale space is.
+If we have a continuous function of a variable such as $f(x)$, then we define the scale space representation of such a function as
+
+\begin{equation}
+L(x;t) = g(x;t) * f(x)
+\end{equation}
+
+Here $t$ represents the scale parameter, and can be thought of how much smoothing is applied to the function. The function $g$ is the Gaussian kernel given by
+
+\begin{equation}
+g(x;t) = \frac{1}{2 \pi t}e^{-(x^2+y^2)/(2t)}
+\end{equation}
 

### 2018-03-05 paper.tex
added to paper

@@
 
-\section{Scale Space}
+\section{Edge Detection}
+    Detecting edges in images has long been a problem with many uniques solutions to approach it.
+Generally speaking, the majority of algorithms are usually checking the image for some of the following features:
+
+    \begin{itemize}
+        \item large discontinuities in luminance values
+        \item discontinuities in different object orientations
+        \item large discontinuities in the intensity gradient
+    \end{itemize}
+
+    \indent Some of the common methods for edge detection include the Sobel, Canny, Prewitt, Roberts, and Fuzzy Logic algorithms.
+However, these methods do not yield a lot of imformation with regards to the strength of the edges detected.
+The majority of these algorithms will usually convolve the image with a static matrix to caclulate edges and does adapt enough to the image.
+
+    This is why for our edge detection method, we will be using the scale space approach.
+The benefit of using a scale space appraoch for edge detection, is we have the ability to classify the strength of the edges in the image.
+This allows for a range of edges from very large immediate changes in intensity to very gradual.
+
+\section{Scale Space and Its Derivatives}
     To understand how exactly we detect images in the scale space, we must first define what the scale space is.
-If we have a continuous function of a variable such as $f(x)$, then we define the scale space representation of such a function as
+If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as
 
     \begin{equation}
-L(x;t) = g(x;t) * f(x)
+        L(x;t) = g(x,y;t) * f(x,y)
     \end{equation}
@@
     \begin{equation}
-g(x;t) = \frac{1}{2 \pi t}e^{-(x^2+y^2)/(2t)}
+        g(x,y;t) = \frac{1}{2 \pi t}e^{-(x^2+y^2)/(2t)}
+    \end{equation}
+
+    With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function. Spatial derivatives are relatively simple being defined as the following
+
+    \begin{equation}
+        L_{x^{\alpha}y^{\beta}}(\cdot;t) = \partial_{x^{\alpha}y^{\beta}}L(\cdot;t) = g_{x^{\alpha}y^{\beta}}(\cdot;t) * f(\cdot)
+    \end{equation}
+
+    However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
+The scale space representation collection is a solution for the diffusion equation.
+Therefore is has the useful property of
+
+    \begin{equation}
+        \partial_t L = \frac{1}{2} \nabla^2 L = \frac{1}{2} (\partial_{xx} + \partial_{yy})L
+    \end{equation}
+
+    with the inital condition of $L(x,y;0) = f(x,y)$. So now, scale derivatives can be represented as spatial derivatives.
+
+    Now all these representations and operators are useful for continuous functions, but the images we deal with are discrete and contain quantized inetsnity values.
+So we must now understand how these operations and properties apply to the discrete domain.
+
+    The scale space representation is still defined in a similar fashion.
+The following is the discrete version of the scale space operationg on the function $f(x)$, which only has a single spatial variable.
+
+    \begin{equation}
+        L(x;t) = (T(\cdot;t) * f(\cdot))(x;t)
+    \end{equation}
+
+    In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as
+
+    \begin{equation}
+        T(n;t) = e^{-t}I_n(t)
+    \end{equation}
+
+    where $I_n$ is the modified Bessel functions of integer order given by
+
+    \begin{equation}
+        I_n(x) = i^{-\alpha}J_{\alpha}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+\alpha+1)}\left(\frac{x}{2}\right)^{2m+\alpha}
+    \end{equation}
+
+    Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
+After all, images are compsed of two dimesnisons, so it makes sense that these operators can act on two dimensional functions.
+The two dimensional scale space representation for discrete variables is given by the follwoing
+
+    \begin{equation}
+        L(x,y;t) = \sum_{m=-\infty}^{\infty}\sum_{n=-\infty}^{\infty}T(m;t)T(n;t)f(x-m,y-n)
+    \end{equation}
+
+    Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
+Therfore by taking a scale derivative of the function we must have the following
+
+    \begin{equation}
+        \partial_t L = \frac{1}{2}((1-\gamma)\nabla^2_5L+\gamma\nabla^2_\times L)
+    \end{equation}
+
+    where
+
+    \begin{equation}
+        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
+    \end{equation}
+    \begin{equation}
+        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
     \end{equation}

### 2018-03-05 paper.tex
updates

@@
 \usepackage{microtype}      % microtypography
+\usepackage{amsmath}
 
@@
 
-\section{Edge Detection}
+\section{Edge Detection Background}
     Detecting edges in images has long been a problem with many uniques solutions to approach it.
@@
 
-    where
+    where $\gamma \in [0,1]$ is a hyperparameter and,
 
     \begin{equation}
-        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
+        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} - 4f_{0,0}
     \end{equation}
     \begin{equation}
-        (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} + 4f_{0,0}
+        (\nabla^2_\times f)_{0,0} = \frac{1}{2}(f_{-1,-1} + f_{-1,+1} + f_{+1,-1} + f_{+1,+1} - 4f_{0,0})
+    \end{equation}
+
+    Note that $f_{-1,1}$ represents $f(x-1, y+1)$. Now that we have defined what discrete scale spaces and their derivatives look like, we can start to define what an edge is.
+
+\section{Defining an Edge in Scale Space}
+    We classify edge points as points which have gradient magnitueds that assume a maximum in the direction of the gradient.
+Let us denote the magnitude of the gradient of $L$ as $L_g$.
+Then we define an edge in the scale space with the following conditions
+
+    \begin{equation} \label{eq:c1}
+        \begin{aligned}
+            L_{gg} &= 0 \\ 
+            L_{ggg} &< 0
+        \end{aligned}
+    \end{equation}
+
+    The way we can then represent these conditions in terms of spatial derivatives is as follows
+
+    \begin{equation}
+        \begin{aligned}
+            L_{gg} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
+            L_{ggg} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
+        \end{aligned}
+    \end{equation}
+
+    This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
+Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space.
+
+    \begin{equation} \label{eq:c2}
+        \begin{aligned}
+            \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
+            \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
+        \end{aligned}
+    \end{equation}
+
+    Then equation \ref{eq:c1} in conjunction with \ref{eq:c2} form the neccessary constraints for us to define an edge in the scale space.
+Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.
+
+    The approach we took was to let our edge strength meteric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor. In this case we can define it as
+
+    \begin{equation}
+        \begin{aligned}
+            G_{\gamma}L &= L_{g,\gamma}^2 \\
+            &= t^{\gamma}(L_x^2+L_y^2)
+        \end{aligned}
     \end{equation}

### 2018-03-05 paper.tex
Updated Julia code for lena picture and colortypes, also paper

@@
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{morefloats}
+\usepackage{float}
+\usepackage{listings}
+\usepackage[usenames,dvipsnames]{xcolor}
+
+    % Define the coloring for keywords in Julia
+    \lstdefinelanguage{Julia}%
+    {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
+        end,export,false,for,function,immutable,import,importall,if,in,%
+        macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
+        using,while},%
+        sensitive=true,%
+        alsoother={$},%
+        morecomment=[l]\#,%
+        morecomment=[n]{\#=}{=\#},%
+        morestring=[s]{"}{"},%
+        morestring=[m]{'}{'},%
+    }[keywords,comments,strings]%
+
+    % Set the lstlistings to the Julia color scheme
+    \lstset{
+        basicstyle=\ttfamily,
+        columns=fullflexible,
+        frame=single,
+        breaklines=true,
+        language         = Julia,
+        basicstyle       = \ttfamily,
+        keywordstyle     = \bfseries\color{blue},
+        stringstyle      = \color{magenta},
+        commentstyle     = \color{ForestGreen},
+        showstringspaces = false,
+    }
 
@@
 
+    Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by
+
+    \begin{equation}
+        G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, ds
+    \end{equation}
+
+    where $ds^2=dx^2+dy^2$.
+
+\section{Implementation}
+    For our implementation we will be using the following image to run our tests on
+
+    \begin{figure}[H]
+    \centering
+        \includegraphics[scale=0.5]{Images/lena.jpg}
+        \caption{Lena Image}
+        \label{lena_o}
+    \end{figure}
+
+    Figure \ref{lena_o} is a standard test image for image processing and is good for our purposes since it contains a variety of different edges with different strengths.
+
+    So what we first do is define our convolution functions that we will be using in code.
+
+    \begin{lstlisting}
+        function combine_kernels(kers...)
+            return reduce(conv2, kers)
+        end
+
+        function convolve_image(I, kers...)
+            kernel = combine_kernels(kers...)
+            return imfilter(I, centered(kernel))
+        end
+
+        function convolve_scale_space(L, kers...)
+            return mapslices(
+                scale_slice -> convolve_image(scale_slice, kers...),
+                L,
+                (1,2)
+            )
+        end
+
+        function convolve_gaussian(img, sigma)
+            # The dimension of the convolution matrix
+            length = 8*ceil(Int, sigma) + 1
+            return imfilter(img, reflect(Kernel.gaussian((sigma, sigma), (length, length))))
+        end
+    \end{lstlisting}
+
 \section*{References}

### 2018-03-05 edge_detect.jl

@@ -10,7 +10,7 @@ gamma = 1
 scales = exp.(linspace(0, log(50), 40))
 
 # Load the image
-img = float.(Colors.Gray.(testimage("mandrill")))
+img = float.(ColorTypes.Gray.(testimage("lena_color_512")))
 
 # Define derivative convolution matrices
 Dy = Array(parent(Kernel.ando5()[1]))

### 2018-03-05 paper.tex
updates

@@
     \lstset{
-        basicstyle=\ttfamily,
-        columns=fullflexible,
-        frame=single,
-        breaklines=true,
+        basicstyle       = \ttfamily,
+        columns          = fullflexible,
+        frame            = single,
+        breaklines       = true,
         language         = Julia,
@@
         showstringspaces = false,
+        numbers          = left,
+        xleftmargin      = 2em,
+        framexleftmargin = 2em
     }
@@
 
+    These will be used for computing all the neccessary two dimensional matrix convolutions that we will use throughout the rest of the code.
+The next step is to then define our range of scales used and which derivative kernels we will be using to compute two dimensional discrete spatial derivatives.
+The following code shows the definitions for our variables that will be used for all further calculations.
+
+    \begin{lstlisting}
+        # Parameters
+        gamma = 1
+        scales = exp.(linspace(0, log(50), 40))
+
+        # Load the image
+        img = float.(ColorTypes.Gray.(testimage("lena_color_512")))
+
+        # Define derivative convolution matrices
+        Dy = Array(parent(Kernel.ando5()[1]))
+        Dx = Array(parent(Kernel.ando5()[2]))
+    \end{lstlisting}
+
 \section*{References}

### 2018-03-05 paper.tex
Fix listings specification

@@
   sensitive=true,%
-        alsoother={$},%
   morecomment=[l]\#,%

### 2018-03-05 paper.tex
stuff
Fix indentation

@@
 \usepackage{amsmath}
+\usepackage{mathtools}
 \usepackage{graphicx}
@@
 
-    With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function. Spatial derivatives are relatively simple being defined as the following
+With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function.
+Spatial derivatives are relatively simple being defined as the following
 
@@
 However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
-The scale space representation collection is a solution for the diffusion equation.
-Therefore is has the useful property of
+The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of
 
@@
 
-    with the inital condition of $L(x,y;0) = f(x,y)$. So now, scale derivatives can be represented as spatial derivatives.
+with the inital condition of $L(x,y;0) = f(x,y)$.
+So now, scale derivatives can be represented as spatial derivatives.
 
@@
 After all, images are compsed of two dimesnisons, so it makes sense that these operators can act on two dimensional functions.
-The two dimensional scale space representation for discrete variables is given by the follwoing
+The two dimensional scale space representation for discrete variables is given by the following
 
@@
 Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
-Therfore by taking a scale derivative of the function we must have the following
+Therefore by taking a scale derivative of the function we must have the following
 
@@
 
-    The approach we took was to let our edge strength meteric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor. In this case we can define it as
+The approach we took was to let our edge strength meteric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor.
+In this case we can define it as
 
@@
   \includegraphics[scale=0.5]{Images/lena.jpg}
-        \caption{Lena Image}
+  \caption{Original Grayscale Lena Image}
   \label{lena_o}
@@
 
+The derivative matrices used for our project are the ando5 matrices which are defined as the following
+
+\begin{equation}
+  \begin{aligned}
+    [D_y] &=
+    \begin{bmatrix}
+      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776 \\
+      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
+      -0.046548 &-0.122572  &0.0  &0.122572  &0.046548 \\
+      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
+      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776
+    \end{bmatrix} \\
+    [D_y] &= [D_x]^T
+  \end{aligned}
+\end{equation}
 \section*{References}

### 2018-03-06 paper.tex
yes
Jon fix this styling when you wake up

@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{commath}
+\usepackage{graphicx}
 
@@
 \begin{equation}
-  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, ds
+  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, \dif s
 \end{equation}
 
-where $ds^2=dx^2+dy^2$.
+where $\dif s^2=\dif x^2+\dif y^2$.
 
@@
 Dx = Array(parent(Kernel.ando5()[2]))
+
+# Normalized the derivatives
+Dx /= sum(Dx .* (Dx .> 0))
+Dy /= sum(Dy .* (Dy .> 0))
 \end{lstlisting}
@@
     \end{bmatrix} \\
-    [D_y] &= [D_x]^T
+    [D_x] &= [D_y]^T
   \end{aligned}
 \end{equation}
+
+From this point, we then can compute the scale space representation of our image and compute its spatial derivatives
+The following section of code defines just how to do that.
+
+\begin{lstlisting}
+# Scale space representation
+L = cat(3, (convolve_gaussian(img, sigma) for sigma in scales)...)
+
+# First order derivatives
+Lx = convolve_scale_space(L, Dx)
+Ly = convolve_scale_space(L, Dy)
+
+# Second order derivatives
+Lxx = convolve_scale_space(Lx, Dx)
+Lxy = convolve_scale_space(Lx, Dy)
+Lyy = convolve_scale_space(Ly, Dy)
+
+# Third order derivatives
+Lxxx = convolve_scale_space(Lxx, Dx)
+Lxxy = convolve_scale_space(Lxx, Dy)
+Lxyy = convolve_scale_space(Lxy, Dy)
+Lyyy = convolve_scale_space(Lyy, Dy)
+\end{lstlisting}
+
+By convolving our ando5 derivative matrix with the scale space representation, we can take spatial derivatives in both the $x$ and $y$ dimension.
+To give an idea of what the images look like, we have the following spatial derivatives of the image below.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.5]{Images/lx.png}
+  \caption{Derivative of image in $x$ direction}
+  \label{lx}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.5]{Images/ly.png}
+  \caption{Derivative of image in $y$ direction}
+  \label{ly}
+\end{figure}
+
+Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
+The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
+The code block below shows the computations for the edge strength based on the gradient magnitued and its derivatives.
+
+\newpage
+
+\begin{lstlisting}
+# Shape the scales vector to be a vector with depth
+scales3 = reshape(scales, 1, 1, length(scales))
+
+# Definition of the gradient edge strength (magnitude)
+const GL = scales3.^(gamma).*(Lx.^2+Ly.^2)
+
+# Derivative of edge strength gradinet with respect to scale
+const GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy))
+
+# Second derivative of edge strength gradinet with respect to scale
+const GLtt = @.
+(gamma*(gamma - 1)*scales3^(gamma - 2)*(Lx^2 + Ly^2) + 2gamma*scales3^(gamma-1)*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy)) + scales3^gamma/2*((Lxxx + Lxyy)^2 + (Lxxy + Lyyy)^2 + Lx*(Lxxxxx + 2Lxxxyy + Lxyyyy) + Ly*(Lxxxxy + 2Lxxyyy + Lyyyyy))) < 0
+\end{lstlisting}
+
+\section*{Appendix}
+
+\lstinputlisting[caption={edge\_detect.jl},label=edge_detect]{edge_detect.jl}
+
 \section*{References}

### 2018-03-06 edge_detect.jl

@@ -72,13 +72,17 @@ Lyyyyy = convolve_scale_space(Lyyy, Dy, Dy)
 const Lvv = @. Lx^2*Lxx + 2Lx*Ly*Lxy + Ly^2*Lyy
 const Lvvv = @. (Lx^3*Lxxx + 3Lx^2*Ly*Lxxy + 3Lx*Ly^2*Lxyy + Ly^3*Lyyy) < 0
 
+# Shape the scales vector to be a vector with depth
 scales3 = reshape(scales, 1, 1, length(scales))
 
+# Definition of the gradient edge strength (magnitude)
+const GL = scales3.^(gamma).*(Lx.^2+Ly.^2)
+
+# Derivative of edge strength gradinet with respect to scale
 const GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy))
 
+# Second derivative of edge strength gradinet with respect to scale
 const GLtt = @. (gamma*(gamma - 1)*scales3^(gamma - 2)*(Lx^2 + Ly^2) + 2gamma*scales3^(gamma-1)*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy)) + scales3^gamma/2*((Lxxx + Lxyy)^2 + (Lxxy + Lyyy)^2 + Lx*(Lxxxxx + 2Lxxxyy + Lxyyyy) + Ly*(Lxxxxy + 2Lxxyyy + Lyyyyy))) < 0
-
-const GL = scales3.^(gamma).*(Lx.^2+Ly.^2)
 
 Z12 = Lvvv .& GLtt
 

### 2018-03-06 paper.tex
damn this appendix is long

@@
 The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
-The code block below shows the computations for the edge strength based on the gradient magnitued and its derivatives.
+The code block below shows the computations for the edge strength based on the gradient magnitude and its derivatives.
 
@@
 
-\lstinputlisting[caption={edge\_detect.jl},label=edge_detect]{edge_detect.jl}
+\lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}
 

### 2018-03-06 edge_detect.jl
Add a signed → [0, 1] clamping function for export

@@ -307,3 +307,9 @@ function main()
     edge_flat = flatten_edges(n_strongest)
     save("output.png", flatten_scale(edge_flat))
 end
+
+clamp_signed(L) = clamp_signed(L, L)
+function clamp_signed(slice, L)
+    min_val, max_val = minimum(L), maximum(L)
+    return @. (slice - min_val)/(max_val - min_val)
+end

### 2018-03-06 edge_detect.jl
Add function to batch export scale space slices

@@ -313,3 +313,9 @@ function clamp_signed(slice, L)
     min_val, max_val = minimum(L), maximum(L)
     return @. (slice - min_val)/(max_val - min_val)
 end
+
+function export_at_scales(L, scale_list, fname)
+    for s in scale_list
+        save((@eval @sprintf($fname, $(scales[s]))), L[:,:,s])
+    end
+end

### 2018-03-06 edge_detect.jl
Rename planar zero finder so name makes more sense

@@ -250,7 +250,7 @@ function flatten_edges(edges)
     return edge_map
 end
 
-function planar_zeros(Lp)
+function spatial_zeros(Lp)
     Lp_pos = signbit.(Lp)
     Lp_zeros = falses(Lp)
     for (i, scale) in enumerate(scales)

### 2018-03-06 edge_detect.jl
Adjust scale range

@@ -7,7 +7,7 @@ using FileIO
 
 # Parameters
 gamma = 1
-scales = exp.(linspace(0, log(50), 40))
+scales = exp.(linspace(log(0.1), log(30), 40))
 
 # Load the image
 img = float.(ColorTypes.Gray.(testimage("lena_color_512")))

### 2018-03-06 edge_detect.jl
Remove superfluous Z1/Z2 declaration

@@ -84,8 +84,6 @@ const GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx +
 # Second derivative of edge strength gradinet with respect to scale
 const GLtt = @. (gamma*(gamma - 1)*scales3^(gamma - 2)*(Lx^2 + Ly^2) + 2gamma*scales3^(gamma-1)*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy)) + scales3^gamma/2*((Lxxx + Lxyy)^2 + (Lxxy + Lyyy)^2 + Lx*(Lxxxxx + 2Lxxxyy + Lxyyyy) + Ly*(Lxxxxy + 2Lxxyyy + Lyyyyy))) < 0
 
-Z12 = Lvvv .& GLtt
-
 function linear_interpolate(p1, p2, v1, v2)
     return (abs(v1)*collect(p1) + abs(v2)*collect(p2))/(abs(v1) + abs(v2))
 end

### 2018-03-06 edge_detect.jl
Add a slice clamping helper function

@@ -312,6 +312,8 @@ function clamp_signed(slice, L)
     return @. (slice - min_val)/(max_val - min_val)
 end
 
+clamp_slices(L) = mapslices(clamp_signed, L, (1,2))
+
 function export_at_scales(L, scale_list, fname)
     for s in scale_list
         save((@eval @sprintf($fname, $(scales[s]))), L[:,:,s])

### 2018-03-06 edge_detect.jl
Make flatten_scale more general

@@ -295,8 +295,8 @@ function n_strongest_edges(edges, n)
     return sort(edges, by=edge_importance, rev=true)[1:n]
 end
 
-function flatten_scale(Lp)
-    return mapslices(any, Lp, 3)
+function flatten_scale(Lp, func=any)
+    return mapslices(func, Lp, 3)
 end
 
 function main()

### 2018-03-06 paper.tex
what is all this crap
yup
fix this pllzzzkzz

@@
 \begin{equation}
-  I_n(x) = i^{-\alpha}J_{\alpha}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+\alpha+1)}\left(\frac{x}{2}\right)^{2m+\alpha}
+  I_n(x) = i^{-n}J_{n}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+n+1)}\left(\frac{x}{2}\right)^{2m+n}
 \end{equation}
@@
 \section{Defining an Edge in Scale Space}
-We classify edge points as points which have gradient magnitueds that assume a maximum in the direction of the gradient.
-Let us denote the magnitude of the gradient of $L$ as $L_g$.
+We classify edge points as points which have gradient magnitude that assume a maximum in the direction of the gradient.
+Let us denote the magnitude of the gradient of $L$ as $L_v$.
 Then we define an edge in the scale space with the following conditions
@@
   \begin{aligned}
-    L_{gg} &= 0 \\
-    L_{ggg} &< 0
+    L_{vv} &= 0 \\
+    L_{vvv} &< 0
   \end{aligned}
@@
   \begin{aligned}
-    L_{gg} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
-    L_{ggg} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
+    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
+    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
   \end{aligned}
@@
 
+The first scale derivative of the gradient magnitude is calculated as follows
+
+\begin{equation}
+  \partial_t (G_{\gamma}L) = \gamma t^{\gamma-1}(L_x^2+L_y^2) + t^{\gamma}(L_x(L_{xxx}+L_{yyy})+L_y(L_{xxy} + L_{yyy}))
+\end{equation}
+
+Then the second scale derivative of the gradient magnitude is
+
+\begin{equation}
+  \begin{align}
+  \partial_{tt} &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
+   &+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
+   &+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2 \\
+   &+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
+   &+L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
+  \end{align}
+\end{equation}
+
 Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by
@@
   \centering
-  \includegraphics[scale=0.5]{Images/lena.jpg}
-  \caption{Original Grayscale Lena Image}
+  \includegraphics[scale=0.5]{Images/lena/lena_orig.png}
+  \caption{Original Lena Image}
   \label{lena_o}
@@
   \begin{aligned}
-    [D_y] &=
+    [D_x] &=
     \begin{bmatrix}
@@
     \end{bmatrix} \\
-    [D_x] &= [D_y]^T
+    [D_y] &= [D_x]^T
   \end{aligned}
@@
 
-\newpage
-
 \begin{lstlisting}
@@
 
+With these calculations we now can check all the conditions necessary to define an edge in scale space.
+
 \section*{Appendix}
 
-\lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}
+% \lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}
 

### 2018-03-07 edge_detect.jl
Use bessel functions to calculate Gaussian kernel

@@ -4,6 +4,7 @@ using ImageView
 using Base.Cartesian
 using ProgressMeter
 using FileIO
+using SpecialFunctions
 
 # Parameters
 gamma = 1
@@ -36,13 +37,19 @@ function convolve_scale_space(L, kers...)
     )
 end
 
-function convolve_gaussian(img, sigma)
-    # The dimension of the convolution matrix
-    length = 8*ceil(Int, sigma) + 1
-    return imfilter(img, reflect(Kernel.gaussian((sigma, sigma), (length, length))))
+function gaussian_kernel(t, length)
+    G = hcat(besselix.(-length:length, t))
+    return reflect(centered(conv2(G, G')))
 end
 
-L = cat(3, (convolve_gaussian(img, sigma) for sigma in scales)...)
+function convolve_gaussian(img, t)
+    # The dimension of the convolution matrix
+    length = 4*ceil(Int, sqrt(t))
+    kernel = gaussian_kernel(t, length)
+    return imfilter(img, kernel)
+end
+
+L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
 
 Lx = convolve_scale_space(L, Dx)
 Ly = convolve_scale_space(L, Dy)

### 2018-03-07 edge_detect.jl
Allow specifying the output filename

@@ -306,11 +306,11 @@ function flatten_scale(Lp, func=any)
     return mapslices(func, Lp, 3)
 end
 
-function main()
+function main(fname="output.png")
     edges = find_edges()
     n_strongest = n_strongest_edges(edges, 500)
     edge_flat = flatten_edges(n_strongest)
-    save("output.png", flatten_scale(edge_flat))
+    save(fname, flatten_scale(edge_flat))
 end
 
 clamp_signed(L) = clamp_signed(L, L)

### 2018-03-07 edge_detect.jl
Increase scale range since sigma = sqrt(t)

@@ -8,7 +8,7 @@ using SpecialFunctions
 
 # Parameters
 gamma = 1
-scales = exp.(linspace(log(0.1), log(30), 40))
+scales = exp.(linspace(log(0.1), log(50*50), 40))
 
 # Load the image
 img = float.(ColorTypes.Gray.(testimage("lena_color_512")))

### 2018-03-07 edge_detect.jl
Optimize the flatten_edges function

@@ -246,11 +246,12 @@ function find_edges()
     return edges
 end
 
-function flatten_edges(edges)
-    edge_flat = reduce(union, edges)
+function flatten_edges(edges, L)
     edge_map = falses((x->x-1).(size(L)))
-    for (x, y, t) in union(edge_flat)
-        edge_map[x,y,t] = true
+    for edge in edges
+        for (x, y, t) in edge
+            edge_map[x,y,t] = true
+        end
     end
     return edge_map
 end
@@ -309,7 +310,7 @@ end
 function main(fname="output.png")
     edges = find_edges()
     n_strongest = n_strongest_edges(edges, 500)
-    edge_flat = flatten_edges(n_strongest)
+    edge_flat = flatten_edges(n_strongest, L)
     save(fname, flatten_scale(edge_flat))
 end
 

### 2018-03-07 edge_detect.jl
Use fastconv to compute more numerically stable small convolutions

@@ -5,13 +5,14 @@ using Base.Cartesian
 using ProgressMeter
 using FileIO
 using SpecialFunctions
+using FastConv # Pkg.clone("https://github.com/aamini/FastConv.jl")
 
 # Parameters
 gamma = 1
 scales = exp.(linspace(log(0.1), log(50*50), 40))
 
 # Load the image
-img = float.(ColorTypes.Gray.(testimage("lena_color_512")))
+img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
 
 # Define derivative convolution matrices
 Dy = Array(parent(Kernel.ando5()[1]))
@@ -21,7 +22,7 @@ Dx /= sum(Dx .* (Dx .> 0))
 Dy /= sum(Dy .* (Dy .> 0))
 
 function combine_kernels(kers...)
-    return reduce(conv2, kers)
+    return reduce(fastconv, kers)
 end
 
 function convolve_image(I, kers...)
@@ -39,7 +40,7 @@ end
 
 function gaussian_kernel(t, length)
     G = hcat(besselix.(-length:length, t))
-    return reflect(centered(conv2(G, G')))
+    return reflect(centered(fastconv(G, G')))
 end
 
 function convolve_gaussian(img, t)

### 2018-03-07 edge_detect.jl
Avoid excessively large scales

@@ -9,7 +9,7 @@ using FastConv # Pkg.clone("https://github.com/aamini/FastConv.jl")
 
 # Parameters
 gamma = 1
-scales = exp.(linspace(log(0.1), log(50*50), 40))
+scales = exp.(linspace(log(0.1), log(256), 40))
 
 # Load the image
 img = float.(ColorTypes.Gray.(load("Images/block.jpg")))

### 2018-03-07 edge_detect.jl
Introduce a spatial derivative helper function

@@ -50,32 +50,30 @@ function convolve_gaussian(img, t)
     return imfilter(img, kernel)
 end
 
+function spatial_derivative(L, x, y)
+    return convolve_scale_space(L, fill(Dx, x)..., fill(Dy, y)...)
+end
+
 L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
 
-Lx = convolve_scale_space(L, Dx)
-Ly = convolve_scale_space(L, Dy)
+Lx = spatial_derivative(L, 1, 0)
+Ly = spatial_derivative(L, 0, 1)
 
-Lxx = convolve_scale_space(Lx, Dx)
-Lxy = convolve_scale_space(Lx, Dy)
-Lyy = convolve_scale_space(Ly, Dy)
+Lxx = spatial_derivative(L, 2, 0)
+Lxy = spatial_derivative(L, 1, 1)
+Lyy = spatial_derivative(L, 0, 2)
 
-Lxxx = convolve_scale_space(Lxx, Dx)
-Lxxy = convolve_scale_space(Lxx, Dy)
-Lxyy = convolve_scale_space(Lxy, Dy)
-Lyyy = convolve_scale_space(Lyy, Dy)
+Lxxx = spatial_derivative(L, 3, 0)
+Lxxy = spatial_derivative(L, 2, 1)
+Lxyy = spatial_derivative(L, 1, 2)
+Lyyy = spatial_derivative(L, 0, 3)
 
-# Lxxxx = convolve_scale_space(Lxxx, Dx)
-# Lxxxy = convolve_scale_space(Lxxx, Dy)
-# Lxxyy = convolve_scale_space(Lxxy, Dy)
-# Lxyyy = convolve_scale_space(Lxyy, Dy)
-# Lyyyy = convolve_scale_space(Lyyy, Dy)
-
-Lxxxxx = convolve_scale_space(Lxxx, Dx, Dx)
-Lxxxxy = convolve_scale_space(Lxxx, Dx, Dy)
-Lxxxyy = convolve_scale_space(Lxxx, Dy, Dy)
-Lxxyyy = convolve_scale_space(Lxxy, Dy, Dy)
-Lxyyyy = convolve_scale_space(Lxyy, Dy, Dy)
-Lyyyyy = convolve_scale_space(Lyyy, Dy, Dy)
[…]

### 2018-03-07 paper.tex
yup

@@
 \end{itemize}
-
 \indent Some of the common methods for edge detection include the Sobel, Canny, Prewitt, Roberts, and Fuzzy Logic algorithms.
@@
 If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as 
-
 \begin{equation}
@@
 \end{equation}
-
 Here $t$ represents the scale parameter, and can be thought of how much smoothing is applied to the function. The function $g$ is the Gaussian kernel given by
-
 \begin{equation}
@@
 \end{equation}
-
 With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function.
 Spatial derivatives are relatively simple being defined as the following
-
 \begin{equation}
@@
 \end{equation}
-
 However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
 The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of 
-
 \begin{equation}
@@
 \end{equation}
-
 with the inital condition of $L(x,y;0) = f(x,y)$.
@@
 The scale space representation is still defined in a similar fashion.
-The following is the discrete version of the scale space operationg on the function $f(x)$, which only has a single spatial variable.
-
+The following is the discrete version of the scale space operating on the function $f(x)$, which only has a single spatial variable.
 \begin{equation}
@@
 \end{equation}
-
 In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as
-
 \begin{equation}
@@
 \end{equation}
-
 where $I_n$ is the modified Bessel functions of integer order given by
-
 \begin{equation}
@@
 \end{equation}
-
 Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
@@
 The two dimensional scale space representation for discrete variables is given by the following
-
 \begin{equation}
@@
 \end{equation}
-
 Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
 Therefore by taking a scale derivative of the function we must have the following
-
 \begin{equation}
@@
 \end{equation}
-
 where $\gamma \in [0,1]$ is a hyperparameter and,
-
 \begin{equation}
@@
 \end{equation}
-
 Note that $f_{-1,1}$ represents $f(x-1, y+1)$. Now that we have defined what discrete scale spaces and their derivatives look like, we can start to define what an edge is.
@@
 \section{Defining an Edge in Scale Space}
-We classify edge points as points which have gradient magnitude that assume a maximum in the direction of the gradient.
-Let us denote the magnitude of the gradient of $L$ as $L_v$.
-Then we define an edge in the scale space with the following conditions
-
+A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
+In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
+Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as
+\begin{equation}
+  \begin{pmatrix}
+    \cos{\alpha} \\
+    \sin{\alpha}
+  \end{pmatrix}
+  = \frac{1}{\sqrt{L_x^2+L_y^2}}
+  \begin{pmatrix}
+    L_x \\
+    L_y
+  \end{pmatrix}
+  \Bigg|_{(x_0,y_0)}
+\end{equation}
+With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system.
+\begin{align}
+  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
+  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
+\end{align}
+So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. So then we define an edge in this coordinate system with the following conditions.
 \begin{equation} \label{eq:c1}
@@
 \end{equation}
-
 The way we can then represent these conditions in terms of spatial derivatives is as follows
-
 \begin{equation}
@@
 \end{equation}
-
 This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
 Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space. 
-
 \begin{equation} \label{eq:c2}
@@
 \end{equation}
-
 Then equation \ref{eq:c1} in conjunction with \ref{eq:c2} form the neccessary constraints for us to define an edge in the scale space.
@@
 In this case we can define it as 
-
-\begin{equation}
-  \begin{aligned}
+\begin{align}
   G_{\gamma}L &= L_{g,\gamma}^2 \\
   &= t^{\gamma}(L_x^2+L_y^2)
-  \end{aligned}
-\end{equation}
-
+\end{align}
 The first scale derivative of the gradient magnitude is calculated as follows
-
 \begin{equation}
@@
 \end{equation}
-
 Then the second scale derivative of the gradient magnitude is
-
 \begin{equation}
-  \begin{align}
+  \begin{aligned}
     \partial_{tt} &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
@@
      &+L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
-  \end{align}
+  \end{aligned}
 \end{equation}
-
 Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by
-
 \begin{equation}
@@
 \end{equation}
-
 where $\dif s^2=\dif x^2+\dif y^2$.
@@
 For our implementation we will be using the following image to run our tests on
-
 \begin{figure}[H]
@@
 \end{figure}
-
 Figure \ref{lena_o} is a standard test image for image processing and is good for our purposes since it contains a variety of different edges with different strengths.
@@
 So what we first do is define our convolution functions that we will be using in code.
-
 \begin{lstlisting}
@@
 \end{lstlisting}
-
 These will be used for computing all the neccessary two dimensional matrix convolutions that we will use throughout the rest of the code.
@@
 The following code shows the definitions for our variables that will be used for all further calculations. 
-
 \begin{lstlisting}
@@
 \end{lstlisting}
-
 The derivative matrices used for our project are the ando5 matrices which are defined as the following
-
 \begin{equation}
@@
 \end{equation}
-
 From this point, we then can compute the scale space representation of our image and compute its spatial derivatives
 The following section of code defines just how to do that.
-
 \begin{lstlisting}
@@
 \end{lstlisting}
-
 By convolving our ando5 derivative matrix with the scale space representation, we can take spatial derivatives in both the $x$ and $y$ dimension.
 To give an idea of what the images look like, we have the following spatial derivatives of the image below.
-
 \begin{figure}[H]
   \centering
-  \includegraphics[scale=0.5]{Images/lx.png}
+  \includegraphics[scale=0.5]{{{Images/lena/lena_Lv_maxima_14.439}}}
   \caption{Derivative of image in $x$ direction}
@@
 \end{figure}
-
 \begin{figure}[H]
   \centering
-  \includegraphics[scale=0.5]{Images/ly.png}
+  \includegraphics[scale=0.5]{Images/lena/lena_final.png}
   \caption{Derivative of image in $y$ direction}
@@
 \end{figure}
-
 Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
@@
 The code block below shows the computations for the edge strength based on the gradient magnitude and its derivatives.
-
 \begin{lstlisting}
@@
 \end{lstlisting}
-
 With these calculations we now can check all the conditions necessary to define an edge in scale space.

### 2018-03-07 paper.tex
Add gradient magnitude table

@@
 \usepackage{graphicx}
+\usepackage{tabu}
 \usepackage{morefloats}
@@
 
+\begin{table}[t]
+  \caption{Gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+
 \section*{Appendix}

### 2018-03-07 paper.tex
HERES UIOTEWHPIUHTEPIWU

@@
 \indent Some of the common methods for edge detection include the Sobel, Canny, Prewitt, Roberts, and Fuzzy Logic algorithms.
-However, these methods do not yield a lot of imformation with regards to the strength of the edges detected.
-The majority of these algorithms will usually convolve the image with a static matrix to caclulate edges and does adapt enough to the image.
+However, these methods do not yield a lot of information with regards to the strength of the edges detected.
+The majority of these algorithms will usually convolve the image with a static matrix to calculate edges and does adapt enough to the image.
 
 This is why for our edge detection method, we will be using the scale space approach.
-The benefit of using a scale space appraoch for edge detection, is we have the ability to classify the strength of the edges in the image.
+The benefit of using a scale space approach for edge detection, is we have the ability to classify the strength of the edges in the image.
 This allows for a range of edges from very large immediate changes in intensity to very gradual.
@@
 \end{equation}
-with the inital condition of $L(x,y;0) = f(x,y)$.
+with the initial condition of $L(x,y;0) = f(x,y)$.
 So now, scale derivatives can be represented as spatial derivatives.
@@
 To give an idea of what the images look like, we have the following spatial derivatives of the image below.
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.5]{{{Images/lena/lena_Lv_maxima_14.439}}}
-  \caption{Derivative of image in $x$ direction}
-  \label{lx}
-\end{figure}
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.5]{Images/lena/lena_final.png}
-  \caption{Derivative of image in $y$ direction}
-  \label{ly}
-\end{figure}
+% \begin{figure}[H]
+%   \centering
+%   \includegraphics[scale=0.5]{{{Images/lena/lena_Lv_maxima_14.439}}}
+%   \caption{Derivative of image in $x$ direction}
+%   \label{lx}
+% \end{figure}
+% \begin{figure}[H]
+%   \centering
+%   \includegraphics[scale=0.5]{Images/lena/lena_final.png}
+%   \caption{Derivative of image in $y$ direction}
+%   \label{ly}
+% \end{figure}
 Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
@@
 
-\begin{table}[t]
+\begin{table}[H]
   \caption{Gradient magnitude}
@@
 \end{table}
+\begin{table}[H]
+  \caption{First scale derivative of gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
 

### 2018-03-07 paper.tex
oh baby a triple

--- 2018-03-07 paper.tex
@@
 
+\begin{table}[H]
+  \caption{Gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{First scale derivative of gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Second scale derivative of the gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Maxima of scale space in the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The second derivative of the scale space with respect to the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The third derivative of the scale space with respect to the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+
 \section*{Appendix}

### 2018-03-09 paper.tex
Add rough draft of marching cubes algorithm

@@
 \usepackage{tabu}
+\usepackage{mathrsfs}
 \usepackage{morefloats}
@@
 \usepackage{graphicx}
+\usepackage{tikz,tikz-3dplot}
+\usetikzlibrary{calc}
+\usetikzlibrary{intersections}
 
@@
 
+\subsection{Marching Cubes}
+
+We note that the equations $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L) =0 $ and $L_{vv} = 0$ define isosurfaces $\mathcal Z_1$ and $\mathcal Z_2$, embedded in $L$.
+Computing the intersection of these two surfaces and requiring the local maxima conditions $\partial_{tt} (\mathcal G_{\text{$\gamma$-norm}} L) < 0$ and $L_{vvv} < 0$ yields a family of isocurves, also embedded in $L$, which directly correspond to the edges in the image.
+
+However, since we only have access to $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L)$ and $L_{vv}$ at the lattice points of $L$, we cannot solve for their intersection analytically.
+Instead, we rely on an approximation method to find the edges.
+We have chosen to implement the algorithm sketched by Lindeberg, a variation of the marching cubes algorithm.
+
+In our implementation, $L$ is broken down into voxels with a value at every corner.
+\begin{lstlisting}
+function marching_cubes(x, y, t, visited)
+    if visited[x, y, t]
+        return Set()
+    end
+
+    visited[x, y, t] = true
+\end{lstlisting}
+Since edges are connected sets of points, we know that if a given voxel has already been visited it cannot be part of this edge, so we skip it.
+
+\begin{lstlisting}
+    const corners = (x:x+1, y:y+1, t:t+1)
+
+    # Note: Maybe they don't need to be in the same corner
+    if !(any(view(GLtt, corners...)) && any(view(Lvvv, corners...)))
+      return Set()
+    end
+\end{lstlisting}
+We then check that our sign conditions $\mathcal S_1 < 0$ and $\mathcal S_2 < 0$ are each negative in at least one vertex of the voxel, otherwise there can be no maxima of $\mathcal Z_1$ and $\mathcal Z_2$ inside this voxel.
+\begin{lstlisting}
+    @views Z1, Z2 = Lvv[corners...], GLt[corners...]
+    Z1_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()
+    Z2_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()
+
+    # Find all sign crossings w/ linear interpolation
+    for (a, b) in cube_edges
+        if signbit(Z1[a...]) != signbit(Z1[b...])
+            push!(Z1_crossings, (a, b, linear_interpolate(a, b, Z1[a...], Z1[b...])))
+        end
+
+        if signbit(Z2[a...]) != signbit(Z2[b...])
+            push!(Z2_crossings, (a, b, linear_interpolate(a, b, Z2[a...], Z2[b...])))
+        end
+    end
+\end{lstlisting}
+
+We then construct a list of edges where the signs of $\mathcal Z_1$ or $\mathcal Z_2$ differ at the endpoints of the edge.
+We then estimate the position of the zero crossing of the surface of that point using linear interpolation.
+\begin{lstlisting}
+    for (normal, face) in cube_faces
+        Z1_zeros, Z2_zeros = [], []
+        for (a, b, mid) in Z1_crossings
+            if a in face && b in face
+                push!(Z1_zeros, mid)
+            end
+        end
+
+        for (a, b, mid) in Z2_crossings
+            if a in face && b in face
+                push!(Z2_zeros, mid)
+            end
+        end
+\end{lstlisting}
+Then, for every face of the voxel, we collect all of the edges with a zero crossing that lie on that face.
+\begin{lstlisting}
+        # Reject if there are more than two crossings for either invariant
+        if !(length(Z1_zeros) == length(Z2_zeros) == 2)
+            continue
+        end
+\end{lstlisting}
+If there is only one edge with a zero crossing on that face, the face cannot have a zero crossing inside it, so we skip further processing on this face.
+If there are four zero crossings of either invariant on this face, then it is ambiguous how the isosurface intersects with the face, so we will skip it\footnote{In the future, we could try to resolve this situation, since there are only two possible cases.} Here is a visualization of one case satisfying these requirements:
+
+\tdplotsetmaincoords{70}{120}
+\begin{center}
+  \begin{tabu}{cc}
+    \toprule
+    $\mathcal Z_1 $(i.e. $L_{vv}$)& $\mathcal Z_2$ (i.e. $\mathcal{G}L_t$)\\
+    \midrule
+    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+      % The vertex at V
+      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+      \tdplotsetcoord{O}{0}{0}{0}
+
+      \draw[]
+      (0,0,0) -- (Px)
+      (0,0,0) -- (Py)
+      (0,0,0) -- (Pz);
+
+      \draw[] (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+      \draw[] (Pyz) -- (Py) -- (Pxy);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (P)!0.63!(Pyz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.45!(Py) $) {};
+      \draw [thick] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxz)!0.4!(Pz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.75!(O) $) {};
+      \draw [thick] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);
+
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
+      \node[label=below left:$+$,fill,circle,inner sep=1.3pt] at (Px) {};
+      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
+      \node[label=above:$-$,fill,circle,inner sep=1.3pt] at (Pz) {};
+      \node[label=below:$+$,fill,circle,inner sep=1.3pt] at (Pxy) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (Pyz) {};
+      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
+    \end{tikzpicture} &
+    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+      % The vertex at V
+      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+      \tdplotsetcoord{O}{0}{0}{0}
+
+      \draw[]
+      (0,0,0) -- (Px)
+      (0,0,0) -- (Py)
+      (0,0,0) -- (Pz);
+
+      \draw[]
+      (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+      \draw[]
+      (Pyz) -- (Py) -- (Pxy);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.63!(Pxz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (O)!0.3!(Pz) $) {};
+      \draw [thick] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.7!(P) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Py)!0.3!(Pyz) $) {};
+
+      \draw [thick] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);
+
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
+      \node[label=below left:$-$,fill,circle,inner sep=1.3pt] at (Px) {};
+      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (Pz) {};
+      \node[label=below:$-$,fill,circle,inner sep=1.3pt] at (Pxy) {};
+      \node[label=above right:$+$,fill,circle,inner sep=1.3pt] at (Pyz) {};
+      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
+    \end{tikzpicture}\\
+    \bottomrule
+  \end{tabu}
+\end{center}
+We then continue our processing:
+\begin{lstlisting}
+        # Check that the intersection lies on a face
+        distance, midpoint = get(intersect)
+        if distance > epsilon || !all(1 - epsilon .<= midpoint .<= 2 + epsilon)
+            continue
+        end
+
+        push!(face_intersections, normal)
+\end{lstlisting}
+We check whether or not the lines caused by connecting the estimated zero crossings of the edges on the face intersect.
+If they do, we mark that face as featuring an intersection, as shown here:
+\begin{center}
+  \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+    % The vertex at V
+    \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+    \tdplotsetcoord{O}{0}{0}{0}
+
+    \draw[]
+    (0,0,0) -- (Px)
+    (0,0,0) -- (Py)
+    (0,0,0) -- (Pz);
+
+    \draw[]
+    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+    \draw[]
+    (Pyz) -- (Py) -- (Pxy);
+
+    \draw[fill,fill opacity=0.15] (P) -- (Pyz) -- (Py) -- (Pxy);
+    \draw[fill,fill opacity=0.15] (O) -- (Pz) -- (Pxz) -- (Px);
+
+    \draw [thick, name path=face1a] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);
+    \draw [thick, name path=face1b] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);
+
+    \draw [thick, name path=face2a] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);
+    \draw [thick, name path=face2b] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);
+
+    \path [name intersections={of=face1a and face1b,by=F1}];
+    \path [name intersections={of=face2a and face2b,by=F2}];
+
+    \node[fill,circle,inner sep=1.7pt] at (F1) {};
+    \node[fill,circle,inner sep=1.7pt] at (F2) {};
+  \end{tikzpicture}
+\end{center}
+Continuing our processing:
+\begin{lstlisting}
+    if length(face_intersections) == 2
+        for normal in face_intersections
+            next_voxel = [x, y, t] + normal
+            if all(1 .<= next_voxel .<= size(visited))
+                union!(result, marching_cubes(next_voxel..., visited))
+            end
+        end
+        push!(result, (x, y, t))
+    end
+\end{lstlisting}
+If there are exactly two faces with zero crossings, then the voxel contains an edge segment.
+We then extend the line defined by connecting the estimated intersection points on each face into the neighboring voxels:
+\begin{center}
+  \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+    % The vertex at V
+    \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+    \tdplotsetcoord{O}{0}{0}{0}
+
+    \draw[]
+    (0,0,0) -- (Px)
+    (0,0,0) -- (Py)
+    (0,0,0) -- (Pz);
+
+    \draw[]
+    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+    \draw[]
+    (Pyz) -- (Py) -- (Pxy);
+
+    \draw[transform canvas={shift={(Py)}}]
+    (0,0,0) -- (Px)
+    (0,0,0) -- (Py)
+    (0,0,0) -- (Pz);
+    \draw[transform canvas={shift={(Py)}}]
+    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+    \draw[transform canvas={shift={(Py)}}]
+    (Pyz) -- (Py) -- (Pxy);
+
+    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
+    (0,0,0) -- (Px)
+    (0,0,0) -- (Py)
+    (0,0,0) -- (Pz);
+    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
+    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
+    (Pyz) -- (Py) -- (Pxy);
+
+    \draw[fill,fill opacity=0.15] (P) -- (Pyz) -- (Py) -- (Pxy);
+    \draw[fill,fill opacity=0.15] (O) -- (Pz) -- (Pxz) -- (Px);
+
+    \draw [dashed, name path=face1a] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);
+    \draw [dashed, name path=face1b] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);
+
+    \draw [dashed, name path=face2a] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);
+    \draw [dashed, name path=face2b] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);
+
+    \path [name intersections={of=face1a and face1b,by=F1}];
+    \path [name intersections={of=face2a and face2b,by=F2}];
+
+    \draw [thick, <->] ($(F1)!-0.5!(F2)$) -- ($(F1)!1.5!(F2)$);
+
+    \node[fill,circle,inner sep=1.7pt] at (F1) {};
+    \node[fill,circle,inner sep=1.7pt] at (F2) {};
+
+  \end{tikzpicture}
+\end{center}
+The process is then repeated on the neighboring voxels until we have traversed the entire edge connected to this point.
+
+% \begin{tikzpicture}[tdplot_main_coords]
+%   % The vertex at V
+%   \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+%   \tdplotsetcoord{O}{0}{0}{0}
+
+%   \draw[thick]
+%   (0,0,0) -- (Px)
+%   (0,0,0) -- (Py)
+%   (0,0,0) -- (Pz);
+
+%   \draw[thick]
+%   (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+%   \draw[thick]
+%   (Pyz) -- (Py) -- (Pxy);
+
+%   \node[label=above:$P$,fill,circle,inner sep=1.75pt] at (P) {};
+%   \node[label=below left:$Px$,fill,circle,inner sep=1.75pt] at (Px) {};
+%   \node[label=below right:$Py$,fill,circle,inner sep=1.75pt] at (Py) {};
+%   \node[label=above:$Pz$,fill,circle,inner sep=1.75pt] at (Pz) {};
+%   \node[label=below:$Pxy$,fill,circle,inner sep=1.75pt] at (Pxy) {};
+%   \node[label=above right:$Pyz$,fill,circle,inner sep=1.75pt] at (Pyz) {};
+%   \node[label=above left:$Pxz$,fill,circle,inner sep=1.75pt] at (Pxz) {};
+%   \node[label=above right:$O$,fill,circle,inner sep=1.75pt] at (O) {};
+% \end{tikzpicture}
 \section*{Appendix}

### 2018-03-10 paper.tex
updated the motivation and introduction

@@
 \begin{abstract}
-  Scale space representation is the idea that a two dimensional image can be represented by a collection of smoothed images.
+  Scale space representation of an image is the idea that a two dimensional image can be represented by a collection of smoothed images.
   This paper documents how using such a representation can be useful for detecting edges in an image.
@@
 
-\section{Edge Detection Background}
-Detecting edges in images has long been a problem with many uniques solutions to approach it.
+\section{Introduction}
+Detecting edges in images has long been a problem with many unique solutions to approach it.
 Generally speaking, the majority of algorithms are usually checking the image for some of the following features:
-
 \begin{itemize}
@@
 \end{itemize}
-\indent Some of the common methods for edge detection include the Sobel, Canny, Prewitt, Roberts, and Fuzzy Logic algorithms.
-However, these methods do not yield a lot of information with regards to the strength of the edges detected.
-The majority of these algorithms will usually convolve the image with a static matrix to calculate edges and does adapt enough to the image.
-
+Common methods for detecting edges in images usually consist of convolving a differential matrix with the image that calculates the image's derivatives in the horizontal or vertical direction.
+Algorithms like the Sobel, Canny, Prewitt, and Robert operators all work in a similar fashion, the only difference being which matrix they convolve with the image.
+The problem with these methods is that they are not very adaptable. 
+They generally will convolve a static matrix that is not dependent on the image, and could be potentially missing out on a lot of information. 
+For example, given an image \textbf{F}, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
+\begin{equation}
+	\textbf{G}_x =
+	\begin{bmatrix}
+		+1 &0 &-1 \\
+		+2 &0 &-2 \\
+		+1 &0 &-1 
+	\end{bmatrix}
+	* \textbf{F}, \;
+	\textbf{G}_y =
+	\begin{bmatrix}
+		+1 &+2 &+1 \\
+		0 &0 &0 \\
+		-1 &-2 &-1 
+	\end{bmatrix}
+	* \textbf{F}
+\end{equation}
 This is why for our edge detection method, we will be using the scale space approach.
@@
 This allows for a range of edges from very large immediate changes in intensity to very gradual.
+
+\section{Motivation}
 
@@
 \section{Defining an Edge in Scale Space}
+\begin{table}[H]
+  \caption{Gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{First scale derivative of gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Second scale derivative of the gradient magnitude}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Maxima of scale space in the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The second derivative of the scale space with respect to the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The third derivative of the scale space with respect to the $v$ direction}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
 A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
@@
      &+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
-     &+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2 \\
+     &+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2\big) \\
      &+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
@@
 With these calculations we now can check all the conditions necessary to define an edge in scale space.
-
-\begin{table}[H]
-  \caption{Gradient magnitude}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[H]
-  \caption{First scale derivative of gradient magnitude}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[H]
-  \caption{Second scale derivative of the gradient magnitude}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[H]
-  \caption{Maxima of scale space in the $v$ direction}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[H]
-  \caption{The second derivative of the scale space with respect to the $v$ direction}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[H]
-  \caption{The third derivative of the scale space with respect to the $v$ direction}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
 

### 2018-03-10 edge_detect.jl
Move derivative operator defs to just before they are first used

@@ -14,13 +14,6 @@ scales = exp.(linspace(log(0.1), log(256), 40))
 # Load the image
 img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
 
-# Define derivative convolution matrices
-Dy = Array(parent(Kernel.ando5()[1]))
-Dx = Array(parent(Kernel.ando5()[2]))
-
-Dx /= sum(Dx .* (Dx .> 0))
-Dy /= sum(Dy .* (Dy .> 0))
-
 function combine_kernels(kers...)
     return reduce(fastconv, kers)
 end
@@ -50,11 +43,18 @@ function convolve_gaussian(img, t)
     return imfilter(img, kernel)
 end
 
+L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
+
+# Define derivative convolution matrices
+Dy = Array(parent(Kernel.ando5()[1]))
+Dx = Array(parent(Kernel.ando5()[2]))
+
+Dx /= sum(Dx .* (Dx .> 0))
+Dy /= sum(Dy .* (Dy .> 0))
+
 function spatial_derivative(L, x, y)
     return convolve_scale_space(L, fill(Dx, x)..., fill(Dy, y)...)
 end
-
-L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
 
 Lx = spatial_derivative(L, 1, 0)
 Ly = spatial_derivative(L, 0, 1)

### 2018-03-10 edge_detect.jl
Move scales definition to just before it is first used

@@ -7,9 +7,8 @@ using FileIO
 using SpecialFunctions
 using FastConv # Pkg.clone("https://github.com/aamini/FastConv.jl")
 
-# Parameters
+# Hyper Parameters
 gamma = 1
-scales = exp.(linspace(log(0.1), log(256), 40))
 
 # Load the image
 img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
@@ -43,6 +42,7 @@ function convolve_gaussian(img, t)
     return imfilter(img, kernel)
 end
 
+scales = exp.(linspace(log(0.1), log(256), 40))
 L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
 
 # Define derivative convolution matrices

### 2018-03-10 paper.tex
Started citations and added bib file

@@
 \usepackage{mathtools}
-\usepackage{graphicx}
+\usepackage[draft]{graphicx}
 \usepackage{tabu}
@@
 \usepackage{tikz,tikz-3dplot}
+\usepackage{longtable}
 \usetikzlibrary{calc}
@@
   columns          = fullflexible,
-  frame            = single,
+  frame            = none,
   breaklines       = true,
@@
 \section{Introduction}
-Detecting edges in images has long been a problem with many unique solutions to approach it.
+
+Detecting edges in images has been a problem in image processing for a long time.
 Generally speaking, the majority of algorithms are usually checking the image for some of the following features:
@@
 \end{itemize}
-Common methods for detecting edges in images usually consist of convolving a differential matrix with the image that calculates the image's derivatives in the horizontal or vertical direction.
-Algorithms like the Sobel, Canny, Prewitt, and Robert operators all work in a similar fashion, the only difference being which matrix they convolve with the image.
+In this paper, we will be using the scale space representation of an image to approach the edge detection problem.
+When we say scale, we refer to how much smoothing has been applied to the image. 
+The theory behind the scale space is that detecting one-dimensional image features, like edges, may be dependent on what scale we operate at \cite{Lindeberg1998}. 
+It follows that we can then define a scale space edge as a set of connected points that:
+\begin{itemize}
+\item have a gradient that takes on a local maximum value in the direction of the gradient\cite{Lindeberg1998}
+\item have an edge strength metric which is a local maximum over various scales\cite{Lindeberg1998}.
+\end{itemize}
+
+\section{Motivation}
+The motivation for this paper comes from observing the difference in quality of the scale space edge detection versus more conventional algorithms.
+Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image that calculates the image's derivatives in the horizontal and vertical directions.
+Algorithms like the Sobel, Canny, Roberts, and Prewitt do just exactly that. 
 The problem with these methods is that they are not very adaptable. 
-They generally will convolve a static matrix that is not dependent on the image, and could be potentially missing out on a lot of information. 
-For example, given an image \textbf{F}, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
+For example, given an image ${F}$, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
 \begin{equation}
-	\textbf{G}_x =
+	{G}_x =
 	\begin{bmatrix}
@@
 	\end{bmatrix}
-	* \textbf{F}, \;
-	\textbf{G}_y =
+	* {F}, \;
+	{G}_y =
 	\begin{bmatrix}
@@
 	\end{bmatrix}
-	* \textbf{F}
+	* {F}
 \end{equation}
-This is why for our edge detection method, we will be using the scale space approach.
-The benefit of using a scale space approach for edge detection, is we have the ability to classify the strength of the edges in the image.
-This allows for a range of edges from very large immediate changes in intensity to very gradual.
-
-\section{Motivation}
+Our algorithm will consist of convolving the ando5 matrix, which is more rotationally symmetric than the other operators listed above, with the image. 
+This convolution will be be performed at multiple scales to evaluate the criteria necessary for classifying a point as an edge point in the scale space. 
+We then run a marching cubes algorithm to connect the local maxima and list our edges based on strength. 
+The ability to list edges and classify their strengths is the main advantage that the scale space edge algorithm has over conventional methods.
 
@@
 \begin{equation}
-  L(x;t) = g(x,y;t) * f(x,y)
+  L(x,y;t) = g(x,y;t) * f(x,y)
 \end{equation}
@@
 However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
-The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of 
+The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of \cite{Lindeberg1993}
 \begin{equation}
@@
 \end{equation}
-In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as
+In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as \cite{Lindeberg1993}
 \begin{equation}
@@
 Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
-Therefore by taking a scale derivative of the function we must have the following
+Therefore by taking a scale derivative of the function we must have the following \cite{Lindeberg1993}
 \begin{equation}
@@
 \section{Defining an Edge in Scale Space}
-\begin{table}[H]
+\begin{table}[h]
   \caption{Gradient magnitude}
+  \label{t_gma}
   \centering
@@
 \end{table}
-\begin{table}[H]
+\begin{table}[h]
   \caption{First scale derivative of gradient magnitude}
+  \label{t_tgma}
   \centering
@@
 \end{table}
-\begin{table}[H]
+\begin{table}[h]
   \caption{Second scale derivative of the gradient magnitude}
+  \label{t_ttgma}
   \centering
@@
 \end{table}
-\begin{table}[H]
+\begin{table}[h]
   \caption{Maxima of scale space in the $v$ direction}
+  \label{t_v}
   \centering
@@
 \end{table}
-\begin{table}[H]
+\begin{table}[h]
   \caption{The second derivative of the scale space with respect to the $v$ direction}
+  \label{t_vv}
   \centering
@@
 \end{table}
-\begin{table}[H]
+\begin{table}[h]
   \caption{The third derivative of the scale space with respect to the $v$ direction}
+  \label{t_vvv}
   \centering
@@
 In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
-Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as
+Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point.
+So then we define necessary angles as \cite{Lindeberg1998}
 \begin{equation}
@@
 \end{equation}
-With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system.
+With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
 \begin{align}
@@
 \end{align}
-So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. So then we define an edge in this coordinate system with the following conditions.
+So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system.
+The results for $L_v$ can be found on page \pageref{t_v}.
+So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
 \begin{equation} \label{eq:c1}
@@
 \end{equation}
-The way we can then represent these conditions in terms of spatial derivatives is as follows
+The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
 \begin{equation}
@@
 \end{equation}
+The results for $L_{vv}$ can be found on page \pageref{t_vv}.
+The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
 This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
-Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space. 
+Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space \cite{Lindeberg1998}
 \begin{equation} \label{eq:c2}
@@
 
-The approach we took was to let our edge strength meteric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor.
-In this case we can define it as 
+The approach we took was to let our edge strength metric be defined by the gradient magnitude that has been normalized by our $\gamma$ factor. 
+Our results for the following calculations can be found on page \pageref{t_gma}.
+In this case we can define our normalized gradient magnitude as \cite{Lindeberg1998}
 \begin{align}
-  G_{\gamma}L &= L_{g,\gamma}^2 \\
+  G_{\gamma}L &= L_{v,\gamma}^2 \\
   &= t^{\gamma}(L_x^2+L_y^2)
 \end{align}
-The first scale derivative of the gradient magnitude is calculated as follows
+
+The first scale derivative of the gradient magnitude results are found on page \pageref{t_tgma}. 
+Its calculations are as follows \cite{Lindeberg1998}
 \begin{equation}
@@
 \end{equation}
-Then the second scale derivative of the gradient magnitude is
+Then the second scale derivative of the gradient magnitude results are found on page \pageref{t_ttgma}.
+Its calculations are as follows \cite{Lindeberg1998}
 \begin{equation}
   \begin{aligned}
-    \partial_{tt} &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
-     &+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
-     &+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2\big) \\
-     &+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
-     &+L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
+    \partial_{tt}(G_{\gamma}L) &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
+     & \hspace{.5pt}+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
+     & \hspace{.5pt}+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2\big) \\
+     & \hspace{.5pt}+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
+     & \hspace{.5pt}+ L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
   \end{aligned}
 \end{equation}
-Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by
+Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by \cite{Lindeberg1998}
 \begin{equation}
@@
 where $\dif s^2=\dif x^2+\dif y^2$.
+
+We then perform a marching cubes algorithm that will connect local points that we have identified as edge points. The details for this can be found on page \pageref{mcube}.
 
@@
 \subsection{Marching Cubes}
-
+\label{mcube}
 We note that the equations $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L) =0 $ and $L_{vv} = 0$ define isosurfaces $\mathcal Z_1$ and $\mathcal Z_2$, embedded in $L$.
@@
 % \end{tikzpicture}
+
 \section*{Appendix}
@@
 
-\section*{References}
+\bibliography{bibliography}{}
+\bibliographystyle{plain}
 

### 2018-03-10 edge_detect.jl
Make the definitions in edge_detect more linearly ordered

@@ -7,12 +7,6 @@ using FileIO
 using SpecialFunctions
 using FastConv # Pkg.clone("https://github.com/aamini/FastConv.jl")
 
-# Hyper Parameters
-gamma = 1
-
-# Load the image
-img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
-
 function combine_kernels(kers...)
     return reduce(fastconv, kers)
 end
@@ -22,25 +16,20 @@ function convolve_image(I, kers...)
     return imfilter(I, centered(kernel))
 end
 
-function convolve_scale_space(L, kers...)
-    return mapslices(
-        scale_slice -> convolve_image(scale_slice, kers...),
-        L,
-        (1,2)
-    )
-end
-
 function gaussian_kernel(t, length)
     G = hcat(besselix.(-length:length, t))
-    return reflect(centered(fastconv(G, G')))
+    return combine_kernels(G, G')
 end
 
 function convolve_gaussian(img, t)
     # The dimension of the convolution matrix
     length = 4*ceil(Int, sqrt(t))
     kernel = gaussian_kernel(t, length)
-    return imfilter(img, kernel)
+    return convolve_image(img, kernel)
 end
+
+# Load the image
+img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
 
 scales = exp.(linspace(log(0.1), log(256), 40))
 L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
@@ -51,6 +40,14 @@ Dx = Array(parent(Kernel.ando5()[2]))
 
 Dx /= sum(Dx .* (Dx .> 0))
 Dy /= sum(Dy .* (Dy .> 0))
+
+function convolve_scale_space(L, kers...)
+    return mapslices(
+        scale_slice -> convolve_image(scale_slice, kers...),
+        L,
+        (1,2)
+    )
+end
 
 function spatial_derivative(L, x, y)
     return convolve_scale_space(L, fill(Dx, x)..., fill(Dy, y)...)
@@ -81,6 +78,10 @@ const Lvvv = @. (Lx^3*Lxxx + 3Lx^2*Ly*Lxxy + 3Lx*Ly^2*Lxyy + Ly^3*Lyyy) < 0
 # Shape the scales vector to be a vector with depth
 scales3 = reshape(scales, 1, 1, length(scales))
 
+# Gamma defines the scale bias, larger numbers = more bias towards diffuse edges.
+# The value 1 represents no bias.
[…]

### 2018-03-10 paper.tex
Remove vestigial merge conflict indicators

@@
 %&pdflatex
-\documentclass{article}
+\documentclass[draft]{article}
 \usepackage[final]{nips_2017}
@@
 \section{Implementation}
-For our implementation we will be using the following image to run our tests on
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.5]{Images/lena/lena_orig.png}
-  \caption{Original Lena Image}
-  \label{lena_o}
-\end{figure}
-Figure \ref{lena_o} is a standard test image for image processing and is good for our purposes since it contains a variety of different edges with different strengths.
 
-So what we first do is define our convolution functions that we will be using in code.
+\subsection{Introduction}
+
+We have chosen to implement our edge detector in the \href{https://julialang.org/}{Julia} scientific computing language.
+We chose Julia because it is very fast and has strong support for linear algebra and image processing through third party packages.
+Our implementation can be found in full at \url{https://github.com/PythonNut/diffgeo-edge-detector}.
+
+\subsection{Convolution Framework}
+
+Both our smoothing and derivative operators are based on discrete approximations represented by convolution matrices.
+Therefore, we implement several convenience functions to apply convolutions to images quickly and with a high degree of numerical stability.
 \begin{lstlisting}
 function combine_kernels(kers...)
-    return reduce(conv2, kers)
+    return reduce(fastconv, kers)
 end
@@
 end
+\end{lstlisting}
 
-function convolve_gaussian(img, sigma)
+Our strategy is to apply convolutions to images in batches.
+For a set $k$ of convolution matrices, we first merge them into a single larger matrix $K$ by reduction via convolution.
+We can do this in any order, since convolutions are associative and commutative.
+We do this using a highly numerically stable convolution algorithm described in \url{https://arxiv.org/abs/1612.08825}.
+% TODO: Cite this paper
+We do this to avoid accumulating numerical errors by repeatedly convolving the image using a less stable algorithm, since the matrices we will be combining are generally small, it is reasonable to use a slower, but more exact algorithm on them.
+
+We then convolve the image with $K$ using a fast tiled FFT algorithm provided by \href{https://github.com/JuliaImages/ImageFiltering.jl}{ImageFiltering.jl}, which is less numerically stable but features faster asymptotic times for large matrices which is helpful as our images can have millions of pixels.
+
+\subsection{Scale Space Generation}
+
+Now, we can generate a tensor representation of scale space.
+\begin{lstlisting}
+function gaussian_kernel(t, length)
+    G = hcat(besselix.(-length:length, t))
+    return combine_kernels(G, G')
+end
+
+function convolve_gaussian(img, t)
     # The dimension of the convolution matrix
-    length = 8*ceil(Int, sigma) + 1
-    return imfilter(img, reflect(Kernel.gaussian((sigma, sigma), (length, length))))
+    length = 4*ceil(Int, sqrt(t))
+    kernel = gaussian_kernel(t, length)
+    return convolve_image(img, kernel)
 end
 \end{lstlisting}
-These will be used for computing all the neccessary two dimensional matrix convolutions that we will use throughout the rest of the code.
-The next step is to then define our range of scales used and which derivative kernels we will be using to compute two dimensional discrete spatial derivatives.
-The following code shows the definitions for our variables that will be used for all further calculations. 
+
+First, we compute a discrete approximation of the gaussian kernel using the bessel function.
+To do this, we take advantage of the separability property of the gaussian kernel, which states that an $N$-dimensional gaussian kernel $g_N$ can be written:
+\[G_N(x_1, \cdots, x_N, t) = G(x_1, t) * \cdots * G(x_N, t)\]
+This allows us to compute a $1$-dimensional gaussian kernel $G$, and produce a $2$-dimensional kernel by convolving $G$ with its transpose.
+
+We then compute an appropriately large kernel size, such that the values of the matrix near the edges are close to the machine epsilon.
+This is important, as we wish to avoid blocking artifacts in our smoothing as a result of our discrete approximation.
+We then apply the generated gaussian kernel to the image.
 \begin{lstlisting}
-# Parameters
-gamma = 1
-scales = exp.(linspace(0, log(50), 40))
+img = float.(ColorTypes.Gray.(load("Images/block.jpg")))
+scales = exp.(linspace(log(0.1), log(256), 40))
+L = cat(3, (convolve_gaussian(img, t) for t in scales)...)
+\end{lstlisting}
 
-# Load the image
-img = float.(ColorTypes.Gray.(testimage("lena_color_512")))
+To generate the scale space itself, we choose a set of 40 scales with uniform effective scale distribution, as described in \url{http://www.diva-portal.org/smash/get/diva2:473381/FULLTEXT01.pdf}.
+% TODO: Cite this
+We then create $40$ copies of the image, and smooth each images by their respective gaussian kernels.
+We then concatenate them to form a rank $3$ tensor representing the scale space.
 
-# Define derivative convolution matrices
+\subsection{Discrete Derivatives}
+We now define our matrix approximations of the derivative operators.
+\begin{lstlisting}
 Dy = Array(parent(Kernel.ando5()[1]))
@@
 
-# Normalized the derivatives
 Dx /= sum(Dx .* (Dx .> 0))
@@
 \end{lstlisting}
-The derivative matrices used for our project are the ando5 matrices which are defined as the following
+
+The derivative matrices used for our project are the $5\times 5$ matrices defined in \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=841757&tag=1}.
+% TODO: Cite this
+Written out, they are:
 \begin{equation}
@@
 \end{equation}
-From this point, we then can compute the scale space representation of our image and compute its spatial derivatives
-The following section of code defines just how to do that.
+Additionally, we normalize the magnitudes of the derivative matrices, such that the sum of the positive values of the matrix sum to $1$, as described in \url{https://link.springer.com/article/10.1007/BF01664794}.
+This is so the overall magnitude of the derivative remains comparable across derivatives of different order.
+% TODO: Cite this.
+We then define a framework for taking the partial derivatives of a scale space in the spatial directions using these operators.
 \begin{lstlisting}
-# Scale space representation
-L = cat(3, (convolve_gaussian(img, sigma) for sigma in scales)...)
+function convolve_scale_space(L, kers...)
+    return mapslices(
+        scale_slice -> convolve_image(scale_slice, kers...),
+        L,
+        (1,2)
+    )
+end
 
-# First order derivatives
-Lx = convolve_scale_space(L, Dx)
-Ly = convolve_scale_space(L, Dy)
+function spatial_derivative(L, x, y)
+    return convolve_scale_space(L, fill(Dx, x)..., fill(Dy, y)...)
+end
+\end{lstlisting}
+To perform spatial convolution, we convolve the scale space independently at every scale.
+To compute $L_{x^iy^j}$ we spatially convolve $i$ times by $[D_x]$ and $j$ times by $[D_y]$.
+Thus, we can compute the higher order partial derivatives of $L$ like so:
+\begin{lstlisting}
+Lx = spatial_derivative(L, 1, 0)
+Ly = spatial_derivative(L, 0, 1)
+# ...
+Lxxyyy = spatial_derivative(L, 2, 3)
+# ...
+\end{lstlisting}
+We calculate all first, second, third, and fifth order spatial partial derivatives of $L$ for use in the future.
 
-# Second order derivatives
-Lxx = convolve_scale_space(Lx, Dx)
-Lxy = convolve_scale_space(Lx, Dy)
-Lyy = convolve_scale_space(Ly, Dy)
+\subsection{Differential Entities}
 
-# Third order derivatives
-Lxxx = convolve_scale_space(Lxx, Dx)
-Lxxy = convolve_scale_space(Lxx, Dy)
-Lxyy = convolve_scale_space(Lxy, Dy)
-Lyyy = convolve_scale_space(Lyy, Dy)
+Now that we have computed the spatial derivatives of the scale space, we can check if we fulfill the conditions described in (Eq. \ref{eq:c1}) and (Eq. \ref{eq:c2}).
+
+\subsubsection{Spatial edge conditions}
+Here is a direct translation of (Eq. \ref{eq:c1}) into Julia.
+\begin{lstlisting}
+Lvv = @. Lx^2*Lxx + 2Lx*Ly*Lxy + Ly^2*Lyy
+Lvvv = @. (Lx^3*Lxxx + 3Lx^2*Ly*Lxxy + 3Lx*Ly^2*Lxyy + Ly^3*Lyyy) < 0
 \end{lstlisting}
-By convolving our ando5 derivative matrix with the scale space representation, we can take spatial derivatives in both the $x$ and $y$ dimension.
-To give an idea of what the images look like, we have the following spatial derivatives of the image below.
-% \begin{figure}[H]
-%   \centering
-%   \includegraphics[scale=0.5]{{{Images/lena/lena_Lv_maxima_14.439}}}
-%   \caption{Derivative of image in $x$ direction}
-%   \label{lx}
-% \end{figure}
-% \begin{figure}[H]
-%   \centering
-%   \includegraphics[scale=0.5]{Images/lena/lena_final.png}
-%   \caption{Derivative of image in $y$ direction}
-%   \label{ly}
-% \end{figure}
-Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
-The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
-The code block below shows the computations for the edge strength based on the gradient magnitude and its derivatives.
+Here, $L_{vv}$ contains the first derivative of the gradient magnitude in the gradient (i.e.
+$v$) direction, and $L_{vvv}$ contains the inverted sign of the second derivative of the magnitude in the $v$ direction.
+These definitions describe the local maxima of of the edge strength with respect to the spatial direction.
+
+\subsubsection{Scale edge conditions}
+Here is a direct translation of (Eq. \ref{eq:c2}) into Julia.
 \begin{lstlisting}
-# Shape the scales vector to be a vector with depth
 scales3 = reshape(scales, 1, 1, length(scales))
-
-# Definition of the gradient edge strength (magnitude)
-const GL = scales3.^(gamma).*(Lx.^2+Ly.^2)
-
-# Derivative of edge strength gradinet with respect to scale
-const GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy))
-
-# Second derivative of edge strength gradinet with respect to scale
-const GLtt = @.
+gamma = 1
+GL = scales3.^(gamma).*(Lx.^2+Ly.^2)
+GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy))
+GLtt = @.
 (gamma*(gamma - 1)*scales3^(gamma - 2)*(Lx^2 + Ly^2) + 2gamma*scales3^(gamma-1)*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy)) + scales3^gamma/2*((Lxxx + Lxyy)^2 + (Lxxy + Lyyy)^2 + Lx*(Lxxxxx + 2Lxxxyy + Lxyyyy) + Ly*(Lxxxxy + 2Lxxyyy + Lyyyyy))) < 0
 \end{lstlisting}
-With these calculations we now can check all the conditions necessary to define an edge in scale space.
+To do this, we transpose the scales array into the third matrix, and then broadcast it across the scale space to form the normalization coefficients.
+
+$\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in the Theory,
+% TODO: reference this
+and $\partial_{tt}(\mathcal G_\gamma L)$ represents the inverted sign of the second partial of $\mathcal G_\gamma L$ with respect to scale.
+These definitions describe the local maxima of of the edge strength with respect to the scale parameter.
 
@@
 \label{mcube}
-We note that the equations $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L) =0 $ and $L_{vv} = 0$ define isosurfaces $\mathcal Z_1$ and $\mathcal Z_2$, embedded in $L$.
+\subsubsection{Introduction}
+We note that the equations $\partial_t (\mathcal G_{\gamma} L) =0 $ and $L_{vv} = 0$ define isosurfaces $\mathcal Z_1$ and $\mathcal Z_2$, embedded in $L$.
 Computing the intersection of these two surfaces and requiring the local maxima conditions $\partial_{tt} (\mathcal G_{\text{$\gamma$-norm}} L) < 0$ and $L_{vvv} < 0$ yields a family of isocurves, also embedded in $L$, which directly correspond to the edges in the image.
 
-However, since we only have access to $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L)$ and $L_{vv}$ at the lattice points of $L$, we cannot solve for their intersection analytically.
-Instead, we rely on an approximation method to find the edges.
+However, since we only have access to $\partial_t (\mathcal G_\gamma L)$ and $L_{vv}$ at the lattice points of $L$, we cannot solve for their intersection analytically.
+Instead, we rely on an approximation algorithm to find the edges.
 We have chosen to implement the algorithm sketched by Lindeberg, a variation of the marching cubes algorithm.
 
+\subsubsection{Geometric Constants}
+To help us, we define the following constants describing the geometry of a cube.
+\begin{lstlisting}
+const cube_edges = [
+    # bottom edges
+    ((1,1,1), (1,2,1)), ((1,2,1), (2,2,1)),
+    ((2,2,1), (2,1,1)), ((2,1,1), (1,1,1)),
+
+    # side edges
+    ((1,1,1), (1,1,2)), ((1,2,1), (1,2,2)),
+    ((2,2,1), (2,2,2)), ((2,1,1), (2,1,2)),
+
+    # top edges
+    ((1,1,2), (1,2,2)), ((1,2,2), (2,2,2)),
+    ((2,2,2), (2,1,2)), ((2,1,2), (1,1,2))
+]
+
+const cube_faces =  [
+  ([ 0, 0,-1], ((1,1,1), (2,1,1), (1,2,1), (2,2,1))),
+  ([ 0,-1, 0], ((1,1,1), (2,1,1), (1,1,2), (2,1,2))),
+  ([ 1, 0, 0], ((2,1,1), (2,1,2), (2,2,2), (2,2,1))),
+  ([-1, 0, 0], ((1,1,1), (1,1,2), (1,2,1), (1,2,2))),
+  ([ 0, 1, 0], ((1,2,1), (2,2,1), (1,2,2), (2,2,2))),
+  ([ 0, 0, 1], ((1,1,2), (1,2,2), (2,2,2), (2,1,2)))
+]
+\end{lstlisting}
+The first defines each edge of the cube as pairs of coordinates, indexing at $1$, as Julia is $1$ indexed.
+The second defines each edge of face of the edge as a pair of the normal vector and the vertices on the corners of that face.
+
+\subsubsection{Recursive Flood Fill}
 In our implementation, $L$ is broken down into voxels with a value at every corner.
+We then use recursion to fill out the edge connected at that point.
 \begin{lstlisting}
@@
 \end{lstlisting}
-Since edges are connected sets of points, we know that if a given voxel has already been visited it cannot be part of this edge, so we skip it.
-
+Since edges are connected sets of points, we know that if a given voxel has already been visited it cannot be part of this edge, so we skip it immediately.
+We next check that our sign conditions $L_{vvv} < 0$ and $\partial_{tt}(\mathcal G_\gamma L) < 0$ are each negative in at least one vertex of the voxel.
 \begin{lstlisting}
@@
 
-    # Note: Maybe they don't need to be in the same corner
     if !(any(view(GLtt, corners...)) && any(view(Lvvv, corners...)))
@@
 \end{lstlisting}
-We then check that our sign conditions $\mathcal S_1 < 0$ and $\mathcal S_2 < 0$ are each negative in at least one vertex of the voxel, otherwise there can be no maxima of $\mathcal Z_1$ and $\mathcal Z_2$ inside this voxel.
+We know that if there is no negative value in the second derivatives, there can be no maxima of $L_{v}$ and $\mathcal G_\gamma L$ inside this voxel, so we skip it immediately.
+Next, we check for zeros of $L_{vv}$ and $\partial_{t} (\mathcal G_\gamma L)$ as indicated by sign changes.
 \begin{lstlisting}
     @views Z1, Z2 = Lvv[corners...], GLt[corners...]
-    Z1_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()
-    Z2_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()
+    Z1_crossings = []
+    Z2_crossings = []
 
@@
 \end{lstlisting}
+To do this, we iterate over every edge.
+Then for each differential entity we check if the endpoints of the edge differ in sign.
+If they do, we estimate the position of the zero crossing of the surface of that point using linear interpolation and save that point along with the edge along with the endpoints of the edge.
+Here is a visualization of one such result:
+\tdplotsetmaincoords{70}{120}
+\begin{center}
+  \begin{tabu}{cc}
+    \toprule
+    $L_{vv}$& $\mathcal{G}L_t$\\
+    \midrule
+    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+      % The vertex at V
+      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+      \tdplotsetcoord{O}{0}{0}{0}
 
-We then construct a list of edges where the signs of $\mathcal Z_1$ or $\mathcal Z_2$ differ at the endpoints of the edge.
-We then estimate the position of the zero crossing of the surface of that point using linear interpolation.
+      \draw[]
+      (0,0,0) -- (Px)
+      (0,0,0) -- (Py)
+      (0,0,0) -- (Pz);
+
+      \draw[] (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+      \draw[] (Pyz) -- (Py) -- (Pxy);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (P)!0.63!(Pyz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.45!(Py) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxz)!0.4!(Pz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.75!(O) $) {};
+
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
+      \node[label=below left:$+$,fill,circle,inner sep=1.3pt] at (Px) {};
+      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
+      \node[label=above:$-$,fill,circle,inner sep=1.3pt] at (Pz) {};
+      \node[label=below:$+$,fill,circle,inner sep=1.3pt] at (Pxy) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (Pyz) {};
+      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
+    \end{tikzpicture} &
+    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
+      % The vertex at V
+      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
+      \tdplotsetcoord{O}{0}{0}{0}
+
+      \draw[]
+      (0,0,0) -- (Px)
+      (0,0,0) -- (Py)
+      (0,0,0) -- (Pz);
+
+      \draw[]
+      (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
+      \draw[]
+      (Pyz) -- (Py) -- (Pxy);
+
+      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.63!(Pxz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (O)!0.3!(Pz) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.7!(P) $) {};
+      \node[fill,circle,inner sep=1.75pt] at ($ (Py)!0.3!(Pyz) $) {};
+
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
+      \node[label=below left:$-$,fill,circle,inner sep=1.3pt] at (Px) {};
+      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
+      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (Pz) {};
+      \node[label=below:$-$,fill,circle,inner sep=1.3pt] at (Pxy) {};
+      \node[label=above right:$+$,fill,circle,inner sep=1.3pt] at (Pyz) {};
+      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
+      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
+    \end{tikzpicture}\\
+    \bottomrule
+  \end{tabu}
+\end{center}
+
+Then, for each face, we determine if there is an intersection of the two isosurfaces on that face.
 \begin{lstlisting}
@@
 \end{lstlisting}
-Then, for every face of the voxel, we collect all of the edges with a zero crossing that lie on that face.
+We collect all of the edges with a zero crossing contained in that face, as defined by its endpoints.
 \begin{lstlisting}
-        # Reject if there are more than two crossings for either invariant
         if !(length(Z1_zeros) == length(Z2_zeros) == 2)
@@
 If there is only one edge with a zero crossing on that face, the face cannot have a zero crossing inside it, so we skip further processing on this face.
-If there are four zero crossings of either invariant on this face, then it is ambiguous how the isosurface intersects with the face, so we will skip it\footnote{In the future, we could try to resolve this situation, since there are only two possible cases.} Here is a visualization of one case satisfying these requirements:
+If there are four zero crossings of either invariant on this face, then the orientation of the zero crossing on that face is ambiguous, so we skip it\footnote{In the future, we could try to resolve this situation, since there are only two possible cases.}.
+If there are exactly two zero crossings on the edges of the face, then we can approximate the zero crossing on that face with the line connecting the two points.
+Here is a visualization of one case satisfying these requirements:
 
@@
     \toprule
-    $\mathcal Z_1 $(i.e. $L_{vv}$)& $\mathcal Z_2$ (i.e. $\mathcal{G}L_t$)\\
+    $L_{vv}$& $\mathcal{G}L_t$\\
     \midrule
@@
 \end{center}
-We then continue our processing:
+
+Next, we check if the lines defined by our two zero conditions intersect.
 \begin{lstlisting}
-        # Check that the intersection lies on a face
+        intersect = segment_intersect(Z1_zeros..., Z2_zeros..., epsilon)
+        if isnull(intersect)
+            continue
+        end
+\end{lstlisting}
+To do this, we calculate the distance between the lines defined by each isosurface.
+If the segments are parallel, the distance is not defined, so we skip the face.
+Next, we check that the lines intersect.
+\begin{lstlisting}
+        const epsilon = 10 * eps()
         distance, midpoint = get(intersect)
@@
 \end{lstlisting}
-We check whether or not the lines caused by connecting the estimated zero crossings of the edges on the face intersect.
-If they do, we mark that face as featuring an intersection, as shown here:
+We do so by checking that the distance between the two lines is close to the machine epsilon, additionally we require that the intersection point of the two lines lies within the face itself.
+If the face fails these conditions, we skip it otherwise we register an intersection on that face.
+Here is a visualization of a case that satisfies our criterion:
 \begin{center}
@@
 \end{center}
-Continuing our processing:
+If there are exactly two faces containing intersections, then the voxel contains an edge segment.
 \begin{lstlisting}
@@
 \end{lstlisting}
-If there are exactly two faces with zero crossings, then the voxel contains an edge segment.
-We then extend the line defined by connecting the estimated intersection points on each face into the neighboring voxels:
+We extend the line defined by connecting the estimated intersection points on each face into the neighboring voxels as shown here:\\[0em]
+
 \begin{center}
@@
 
-  \end{tikzpicture}
+  \end{tikzpicture}\\[1.5em]
 \end{center}
-The process is then repeated on the neighboring voxels until we have traversed the entire edge connected to this point.
+
+The process is then repeated on the neighboring voxels as defined by the extrapolation.
+This allows us to recursively trace out the full connected edge at this point.
 

### 2018-03-10 paper.tex
Move epsilon definition to fix error

@@
 \begin{lstlisting}
+        const epsilon = 10 * eps()
         intersect = segment_intersect(Z1_zeros..., Z2_zeros..., epsilon)
@@
 \begin{lstlisting}
-        const epsilon = 10 * eps()
         distance, midpoint = get(intersect)

### 2018-03-10 edge_detect.jl

@@ -203,13 +203,13 @@ function marching_cubes(x, y, t, visited)
         end
 
         # Check the intersection of the segments defined by the two lines
+        const epsilon = 10 * eps()
         distance_check = line_distance(Z1_zeros..., Z2_zeros..., epsilon)
         if isnull(distance_check)
             continue
         end
 
         # Check that the intersection lies on a face
-        const epsilon = 10 * eps()
         distance, midpoint = get(distance_check)
         if distance > epsilon || !all(1 - epsilon .<= midpoint .<= 2 + epsilon)
             continue

### 2018-03-10 paper.tex
all citations added

@@
 %&pdflatex
-\documentclass[draft]{article}
+\documentclass{article}
 \usepackage[final]{nips_2017}
@@
 \usepackage{mathtools}
-\usepackage[draft]{graphicx}
+\usepackage{graphicx}
 \usepackage{tabu}
@@
 \author{
-  Nick Draper, Jonathan Hayase\\
+  Nicholas Draper, Jonathan Hayase\\
   Seminar in Differential Geometry\\
@@
   This paper documents how using such a representation can be useful for detecting edges in an image.
-  The scale space allows for a classification of how strong different edges are in the image from very fine to coarse ones. 
+  In addition to the theory, this paper also covers an in depth implementation of the algorithm written in the Julia programming language.
 \end{abstract}
@@
 \section{Introduction}
-
-Detecting edges in images has been a problem in image processing for a long time.
-Generally speaking, the majority of algorithms are usually checking the image for some of the following features:
+Detecting edges in images has long been a persistent problem in image processing.  
+Generally speaking, the majority of algorithms usually detect edges by identifying at least one of the following features:
 \begin{itemize}
@@
 In this paper, we will be using the scale space representation of an image to approach the edge detection problem.
-When we say scale, we refer to how much smoothing has been applied to the image. 
-The theory behind the scale space is that detecting one-dimensional image features, like edges, may be dependent on what scale we operate at \cite{Lindeberg1998}. 
+Scale refers to how much smoothing is applied to the image. 
+The theory behind the scale space representation is that detecting one-dimensional image features, like edges, may be dependent on what scale we operate at \cite{Lindeberg1998}. 
 It follows that we can then define a scale space edge as a set of connected points that:
@@
 \section{Motivation}
-The motivation for this paper comes from observing the difference in quality of the scale space edge detection versus more conventional algorithms.
-Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image that calculates the image's derivatives in the horizontal and vertical directions.
+The motivation for this paper comes from observing how much the scale affects the detection of edges in an image. 
+Most common edge detection algorithms are applied only at a scale of zero, i.e. the original image.
+Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image to calculate spatial derivatives of the image.
 Algorithms like the Sobel, Canny, Roberts, and Prewitt do just exactly that. 
-The problem with these methods is that they are not very adaptable. 
+The problem with these methods is that they are not very adaptable, and they could be possibly neglecting useful information at other scales. 
 For example, given an image ${F}$, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
@@
 We then run a marching cubes algorithm to connect the local maxima and list our edges based on strength. 
-The ability to list edges and classify their strengths is the main advantage that the scale space edge algorithm has over conventional methods.
+The ability to list edges and classify their strengths is one of the advantages that the scale space edge algorithm has over conventional methods.
 
@@
 To understand how exactly we detect images in the scale space, we must first define what the scale space is.
-If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as 
+If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as the following convolution
 \begin{equation}
@@
 Its calculations are as follows \cite{Lindeberg1998}
-\begin{equation}
+\begin{equation} \label{dtGl}
   \partial_t (G_{\gamma}L) = \gamma t^{\gamma-1}(L_x^2+L_y^2) + t^{\gamma}(L_x(L_{xxx}+L_{yyy})+L_y(L_{xxy} + L_{yyy}))
@@
 We can do this in any order, since convolutions are associative and commutative.
-We do this using a highly numerically stable convolution algorithm described in \url{https://arxiv.org/abs/1612.08825}.
-% TODO: Cite this paper
+We do this using a highly numerically stable convolution algorithm described in \cite{Amini}.
 We do this to avoid accumulating numerical errors by repeatedly convolving the image using a less stable algorithm, since the matrices we will be combining are generally small, it is reasonable to use a slower, but more exact algorithm on them.
@@
 
-To generate the scale space itself, we choose a set of 40 scales with uniform effective scale distribution, as described in \url{http://www.diva-portal.org/smash/get/diva2:473381/FULLTEXT01.pdf}.
-% TODO: Cite this
+To generate the scale space itself, we choose a set of 40 scales with uniform effective scale distribution, as described in \cite{Lindeberg1993b}.
 We then create $40$ copies of the image, and smooth each images by their respective gaussian kernels.
@@
 
-The derivative matrices used for our project are the $5\times 5$ matrices defined in \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=841757&tag=1}.
-% TODO: Cite this
+The derivative matrices used for our project are the $5\times 5$ matrices defined in \cite{Ando}.
 Written out, they are:
@@
 \end{equation}
-Additionally, we normalize the magnitudes of the derivative matrices, such that the sum of the positive values of the matrix sum to $1$, as described in \url{https://link.springer.com/article/10.1007/BF01664794}.
+Additionally, we normalize the magnitudes of the derivative matrices, such that the sum of the positive values of the matrix sum to $1$, as described in \cite{Lindeberg1993}.
 This is so the overall magnitude of the derivative remains comparable across derivatives of different order.
-% TODO: Cite this.
+
 We then define a framework for taking the partial derivatives of a scale space in the spatial directions using these operators.
@@
 
-$\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in the Theory,
-% TODO: reference this
+$\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in (Eq.
+\ref{Gl})
 and $\partial_{tt}(\mathcal G_\gamma L)$ represents the inverted sign of the second partial of $\mathcal G_\gamma L$ with respect to scale.

### 2018-03-10 paper.tex
updated

@@
 $\mathcal G_\gamma L$ represents the normalized gradient magnitude, which serves as our edge strength measure, $\partial_t(\mathcal G_\gamma L)$ represents the first partial of $\mathcal G_\gamma L$ with respect to the scale parameter as described in (Eq.
-\ref{Gl})
+\ref{dtGl})
 and $\partial_{tt}(\mathcal G_\gamma L)$ represents the inverted sign of the second partial of $\mathcal G_\gamma L$ with respect to scale.

### 2018-03-10 paper.tex
sjtjhsr

@@
 \begin{itemize}
-\item have a gradient that takes on a local maximum value in the direction of the gradient\cite{Lindeberg1998}
+\item have a gradient that assumes a local maximum value in the direction of the gradient\cite{Lindeberg1998}
 \item have an edge strength metric which is a local maximum over various scales\cite{Lindeberg1998}.
@@
 \section{Scale Space and Its Derivatives}
-To understand how exactly we detect images in the scale space, we must first define what the scale space is.
+To understand how exactly we detect edges in the scale space, we must first define what the scale space is.
 If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as the following convolution
@@
 with the initial condition of $L(x,y;0) = f(x,y)$.
-So now, scale derivatives can be represented as spatial derivatives.
+So we can now represent scale derivatives as spatial derivatives.
 
-Now all these representations and operators are useful for continuous functions, but the images we deal with are discrete and contain quantized inetsnity values.
+Now all these representations and operators are useful for continuous functions, but the images we deal with are discrete and contain quantized intensity values.
 So we must now understand how these operations and properties apply to the discrete domain.
@@
 The scale space representation is still defined in a similar fashion.
-The following is the discrete version of the scale space operating on the function $f(x)$, which only has a single spatial variable.
+The following is the discrete version of the scale space operating on the function $f(x)$
 \begin{equation}
@@
 Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
-After all, images are compsed of two dimesnisons, so it makes sense that these operators can act on two dimensional functions.
+After all, images are composed of two dimensions, so it makes sense that these operators can act on two dimensional functions.
 The two dimensional scale space representation for discrete variables is given by the following
@@
 \section{Defining an Edge in Scale Space}
-\begin{table}[h]
-  \caption{Gradient magnitude}
-  \label{t_gma}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[h]
-  \caption{First scale derivative of gradient magnitude}
-  \label{t_tgma}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[h]
-  \caption{Second scale derivative of the gradient magnitude}
-  \label{t_ttgma}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[h]
-  \caption{Maxima of scale space in the $v$ direction}
-  \label{t_v}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[h]
-  \caption{The second derivative of the scale space with respect to the $v$ direction}
-  \label{t_vv}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
-\begin{table}[h]
-  \caption{The third derivative of the scale space with respect to the $v$ direction}
-  \label{t_vvv}
-  \centering
-  \tabulinesep=0.1em
-  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
-    \toprule
-    & Lena & Mandrill & Peppers\\
-    \midrule
-    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_0.1}}}\\
-    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_1.7}}}\\
-    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_18.7}}}\\
-    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_93.6}}}\\
-    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_256.0}}}\\
-    \bottomrule
-\end{tabu}
-\end{table}
 A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
@@
 This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
-Thus this adds two more conditions that must be satisified for an edge to be classified in the scale space \cite{Lindeberg1998}
+Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
 \begin{equation} \label{eq:c2}
@@
 \section*{Appendix}
-
+\begin{table}[H]
+  \caption{Gradient magnitude}
+  \label{t_gma}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GL_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GL_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GL_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GL_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{First scale derivative of gradient magnitude}
+  \label{t_tgma}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Second scale derivative of the gradient magnitude}
+  \label{t_ttgma}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_GLtt_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_GLtt_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_GLtt_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{Maxima of scale space in the $v$ direction}
+  \label{t_v}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lv_maxima_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lv_maxima_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lv_maxima_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The second derivative of the scale space with respect to the $v$ direction}
+  \label{t_vv}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
+\begin{table}[H]
+  \caption{The third derivative of the scale space with respect to the $v$ direction}
+  \label{t_vvv}
+  \centering
+  \tabulinesep=0.1em
+  \begin{tabu}to \textwidth{cX[c,m]X[c,m]X[c,m]}
+    \toprule
+    & Lena & Mandrill & Peppers\\
+    \midrule
+    $t = 0.1$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_0.1}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_0.1}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_0.1}}}\\
+    $t = 1.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_1.7}}} & \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_1.7}}}\\
+    $t = 18.7$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_18.7}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_18.7}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_18.7}}}\\
+    $t = 93.6$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_93.6}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_93.6}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_93.6}}}\\
+    $t = 256.0$ & \includegraphics[height=11em]{{{Images/lena/lena_Lvvv_256.0}}} & \includegraphics[height=11em]{{{Images/mandrill/mandrill_Lvvv_256.0}}} &  \includegraphics[height=11em]{{{Images/peppers/peppers_Lvvv_256.0}}}\\
+    \bottomrule
+\end{tabu}
+\end{table}
 % \lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}

### 2018-03-10 paper.tex
updated equation format
Add results section

@@
 \end{equation}
-Then equation \ref{eq:c1} in conjunction with \ref{eq:c2} form the neccessary constraints for us to define an edge in the scale space.
+Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
 Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.
@@
 
+\section{Results}
+\subsection{Diffuse and sharp edges in the same photo}
+To demonstrate the results of our program, we will use the following test image.
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.3]{Images/block/block_orig.jpg}
+  \caption{Block test image}
+  \label{block_orig}
+\end{figure}
+
+Here is the result of thresholding the gradient as calculated by the Sobel operator for this image:
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.3]{Images/block/sobel_block.jpg}
+  \caption{The edges of the block image according to the Sobel gradient}
+  \label{block_sobel}
+\end{figure}
+
+In contrast, our edge detection algorithm produces the following result:
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.3]{Images/block/block_final.png}
+  \caption{The final output of our program on the block image}
+  \label{block_final}
+\end{figure}
+The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
+Unfortunately, the edge of the shadow is not a continuous path.
+This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
+We can see this by displaying the full set of edges:
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
+  \caption{All edges of the block image as detected by our program}
+  \label{block_final}
+\end{figure}
+In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.
+
+\subsection{Other results}
+Subjectively, our results seem quite reasonable for the given inputs.
+Further improvement can be made to fix spurious edge segmentation in the future.
+\begin{table}[H]
+  \caption{Results of running our program on other images}
+  \label{t_vvv}
+  \centering
+  \tabulinesep=0.3em
+  \begin{tabu}to \textwidth{X[c,m]X[c,m]}
+    \toprule
+    Original & Result\\
+    \midrule
+    \includegraphics[height=18em]{{{Images/lena/lena_orig}}} & \includegraphics[height=18em]{{{Images/lena/lena_final}}} \\
+    \includegraphics[height=18em]{{{Images/mandrill/mandrill_orig}}} & \includegraphics[height=18em]{{{Images/mandrill/mandrill_final}}} \\
+    \includegraphics[height=18em]{{{Images/peppers/peppers_orig}}} & \includegraphics[height=18em]{{{Images/peppers/peppers_final}}} \\
+    \bottomrule
+  \end{tabu}
+\end{table}
+
 \section*{Appendix}

### 2018-03-10 paper.tex
spelling

@@
 \section{Defining an Edge in Scale Space}
-A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
+A useful system to use when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
 In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.

### 2018-03-10 paper.tex
Fix block_all_edges label
Add edge selection subsection to implementation

@@
 
+Then, to find all edges in the image, we simply run the marching cubes algorithm on every voxel in the image like so:
+\begin{lstlisting}
+function find_edges()
+    voxel_visited = falses((x->x-1).(size(L)))
+    edges = []
+    p = Progress(prod(size(voxel_visited)), 1)
+    @nloops 3 i voxel_visited begin
+        edge = marching_cubes((@ntuple 3 i)..., voxel_visited)
+        if length(edge) > 0
+            push!(edges, edge)
+        end
+        next!(p)
+    end
+    return edges
+end
+\end{lstlisting}
+
+\subsection{Selecting images by strength}
+
+Now that we have found all scale space edges, it remains to select an ``interesting'' subset of them to display.
+To do this, we rank the edges by their integrated edge strength as described in the Theory and take the first $n$ of them to be sufficiently important to display.
+% TODO: fix this
+\begin{lstlisting}
+function edge_importance(edge)
+    total = 0
+    for (x, y, t) in edge
+        total += sqrt(GL[x,y,t])
+    end
+    return total
+end
+
+function n_strongest_edges(edges, n)
+    return sort(edges, by=edge_importance, rev=true)[1:n]
+end
+\end{lstlisting}
+
+We then have a function to flatten the edge sets back into scale space by iterating though them and forming a boolean tensor if there is a edge inside that voxel.
+\begin{lstlisting}
+function flatten_edges(edges, L)
+    edge_map = falses((x->x-1).(size(L)))
+    for edge in edges
+        for (x, y, t) in edge
+            edge_map[x,y,t] = true
+        end
+    end
+    return edge_map
+end
+\end{lstlisting}
+
+Finally, we flatten the boolean tensor into an image by taking the logical disjunction of all values at a given spatial location in the image.
+\begin{lstlisting}
+function flatten_scale(Lp, func=any)
+    return mapslices(func, Lp, 3)
+end
+\end{lstlisting}
+
 \section{Results}
@@
   \caption{All edges of the block image as detected by our program}
-  \label{block_final}
+  \label{block_all_edges}
 \end{figure}

### 2018-03-10 paper.tex
done

@@
 \section{Introduction}
-Detecting edges in images has long been a persistent problem in image processing.  
+Detecting edges in images has been a common problem in image processing.  
 Generally speaking, the majority of algorithms usually detect edges by identifying at least one of the following features:
@@
 Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image to calculate spatial derivatives of the image.
-Algorithms like the Sobel, Canny, Roberts, and Prewitt do just exactly that. 
-The problem with these methods is that they are not very adaptable, and they could be possibly neglecting useful information at other scales. 
+Algorithms like the Sobel, Canny, Roberts, and Prewitt perform such an operation. 
+The problem with these methods is that they are not very adaptable, and they could neglect useful information at other scales. 
 For example, given an image ${F}$, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
@@
 \end{equation}
-Our algorithm will consist of convolving the ando5 matrix, which is more rotationally symmetric than the other operators listed above, with the image. 
+Our algorithm will consist of convolving the $5 \times 5$ matrix, which is more rotationally symmetric than the other operators listed above, with the image. 
 This convolution will be be performed at multiple scales to evaluate the criteria necessary for classifying a point as an edge point in the scale space. 
 We then run a marching cubes algorithm to connect the local maxima and list our edges based on strength.
-The ability to list edges and classify their strengths is one of the advantages that the scale space edge algorithm has over conventional methods.
 
 \section{Scale Space and Its Derivatives}
-To understand how exactly we detect edges in the scale space, we must first define what the scale space is.
+To understand how edges are defined in scale space, we must first define what the scale space is.
 If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as the following convolution
@@
 Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
-After all, images are composed of two dimensions, so it makes sense that these operators can act on two dimensional functions.
 The two dimensional scale space representation for discrete variables is given by the following
@@
 A useful system to use when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
-In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
+Here we setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
 Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point.
@@
 \end{equation}
-With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
+With our angle defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
 \begin{align}
@@
 Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by \cite{Lindeberg1998}
-\begin{equation}
+\begin{equation} \label{estr}
   G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, \dif s
@@
 Now that we have found all scale space edges, it remains to select an ``interesting'' subset of them to display.
-To do this, we rank the edges by their integrated edge strength as described in the Theory and take the first $n$ of them to be sufficiently important to display.
+To do this, we rank the edges by their integrated edge strength as described in (Eq. \ref{estr}) and take the first $n$ of them to be sufficiently important to display.
 % TODO: fix this
@@
   \centering
-  \includegraphics[scale=0.3]{Images/block/block_orig.jpg}
+  \includegraphics[scale=0.36]{Images/block/block_orig.jpg}
   \caption{Block test image}
@@
   \centering
-  \includegraphics[scale=0.3]{Images/block/sobel_block.jpg}
+  \includegraphics[scale=0.36]{Images/block/sobel_block.jpg}
   \caption{The edges of the block image according to the Sobel gradient}
@@
   \centering
-  \includegraphics[scale=0.3]{Images/block/block_final.png}
+  \includegraphics[scale=0.36]{Images/block/block_final.png}
   \caption{The final output of our program on the block image}
@@
   \centering
-  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
+  \includegraphics[scale=0.36]{Images/block/block_all_edges.png}
   \caption{All edges of the block image as detected by our program}
@@
   \caption{Results of running our program on other images}
-  \label{t_vvv}
+  \label{results}
   \centering
@@
 \section*{Appendix}
+Note all images here are normalized, so only relative differences within the same image are relevant.
 \begin{table}[H]
